### 2024-09-16 src/amr_control/docs/paper.tex
New Plot, Folder for rosbags

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{blindtext}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{caption}
\usepackage[numbers,sort&compress]{natbib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em

    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

% Create custom colour for text highlighting
\definecolor{twblue}{HTML}{1f497d}
\definecolor{structure}{HTML}{1f497d}
\definecolor{blindtext}{HTML}{D3D3D3}

\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage} % Seitenzahl im rechten Fuß

\title{ EVALUATING MODEL PREDICTIVE CONTROL IN DIFFERENTIAL DRIVE ROBOTICS: \\ COMPREHENSIVE LITERATURE REVIEW }

\author{\IEEEauthorblockN{\textbf{Student:} Eppacher Kevin, BSc. \textbf{PK:} 2310331013}
        \IEEEauthorblockN{\textbf{Peer ReviewerIn:} Schweiger Simon, MSc.}
}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
    Mobile robots are widely used in industries, households, and public spaces, such as Autonomous
    Mobile Robots (AMRs) for transporting goods in intralogistics, vacuum/mower robots, and service
    robots in restaurants. However, mobile robots face several challenges, including highly dynamic
    environments, external disturbances such as slippage, which can complicate localization over 
    long distances, and other environmental factors. The goal of this work is to develop a system that 
    enables a mobile robot to navigate optimally and collision-free. Several established approaches,
    such as the Dynamic Window Approach (DWA) and Move Base Flex, have already proven effective.
    The Dynamic Window Approach limits the robot's velocity space to ensure collision avoidance, while
    Move Base Flex provides a flexible interface for path planning and execution, allowing for the 
    integration of different navigation frameworks. In this work, a control system is developed for 
    dynamic obstacle avoidance using a nonlinear Model Predictive Controller (nMPC). The results are 
    compared with the well-established Move Base DWA from ROS1. Both controllers are evaluated in a 
    Gazebo simulation under three conditions: with static objects, with dynamically detected obstacles, 
    and without obstacle avoidance (i.e., without laser scan).

    (Results will follow...)
\end{abstract}

\begin{IEEEkeywords}
Model Predictive Control, Differential Drive Robots, Obstacle Avoidance, Autonomous Mobile Robots, Control Algorithms
\end{IEEEkeywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
% Introduction to the paper’s main subject (subject = lokale Pfadplanung)

Mobile robots are becoming increasingly indispensable in various fields such as intralogistics, public, and private services, with applications ranging from autonomous floor-cleaning robots to vacuum cleaners. In dynamic environments, these robots are frequently confronted with fast-moving obstacles, which they must detect and avoid in real-time. The conventional approach to navigation involves the mobile robot first creating a map of its surroundings, typically using an occupancy grid to store information about static objects such as walls. Based on this map, a global path is planned using algorithms such as Rapidly Exploring Random Tree (RRT), which the robot subsequently follows \cite{thrun2005probabilistic}.

However, it is important to note that while the global path provides an initial route, it is updated at a lower frequency compared to the local planner, which operates at a higher update rate. The local planner is responsible for adjusting the robot's trajectory in real-time to avoid newly detected obstacles, while still adhering to the waypoints of the global path \cite{siegwart2011autonomous}. This separation between global path planning and local obstacle avoidance is critical in ensuring that the robot can navigate effectively in both known and dynamic environments \cite{khatib1986real}.

% Motivation for creating paper contribution (sehr grobe Übersicht über sota)

The Dynamic Window Approach (DWA) efficiently computes safe velocities by evaluating a limited set of possible trajectories. However, it lacks long-term trajectory optimization and struggles with dynamic obstacles due to its short prediction horizon. In contrast, nMPC optimizes over a longer horizon, allowing for more accurate predictions and better handling of dynamic environments.

The Timed Elastic Band (TEB) planner adjusts global paths to account for dynamic obstacles and kinodynamic constraints but can suffer from high computational demands in dense or highly dynamic environments. nMPC provides a more computationally efficient solution by directly incorporating system dynamics and constraints into the optimization process, improving real-time performance in dynamic environment.

Move Base Flex (MBF) offers flexibility by integrating various local planners, such as DWA and TEB, but inherits their limitations in obstacle avoidance. By integrating nMPC into MBF, a more robust solution can be achieved, as nMPC offers superior handling of nonlinear dynamics and dynamic obstacle avoidance.

% Problem description arising from motivation (was fehlt im aktuellen sota -> vermeidung dynamischer Objekte)
Current local planners, such as the widely used Dynamic Window Approach (DWA) in the ROS Navigation stack, are effective for static and slow-moving obstacles but fail in dynamic environments with fast-moving obstacles. These planners lack the ability to predict and react effectively to rapidly changing environments, leading to suboptimal performance in real-time obstacle avoidance.

% Paper contribution
This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance. The primary contribution is the integration of nMPC to improve real-time navigation performance in dynamic environments. Unlike conventional approaches such as DWA, the proposed nMPC effectively handles nonlinear dynamics and dynamic obstacles, offering superior prediction accuracy and responsiveness.

This paper contributes to the field by rigorously evaluating the nMPC against both DWA and recent advancements in local planning algorithms from the past five years. The results demonstrate that the nMPC provides enhanced trajectory optimization and obstacle avoidance capabilities, filling a crucial gap in mobile robot control by addressing scenarios that existing methods have not sufficiently solved.

% Paper structure
The rest of the paper is organized as follows: Section II discusses related work in local path planning and obstacle avoidance. Section III outlines the methodology used for our comparative evaluation. Section IV presents the results of simulations, and Section V concludes with a summary of findings and potential future research directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State-of-the-Art}

In this section, we provide an overview of several state-of-the-art local planners, including the Dynamic Window Approach (DWA), Timed Elastic Band (TEB), Model Predictive Control (MPC), Move Base Flex (MBF), Agile and Safe Pursuit (ASAP), and Reinforcement Learning (RL)-based planners. We explain how these planners function and highlight their key limitations, especially when operating in dynamic environments. Additionally, we discuss how nonlinear Model Predictive Control (nMPC) addresses these limitations and provides improved performance.

\subsection{Dynamic Window Approach (DWA)}
DWA is a popular local planner that selects safe and feasible velocities by sampling translational \((v)\) and rotational \((\omega)\) velocities within a dynamic window. These sampled velocities are evaluated through an objective function that balances forward movement and obstacle avoidance. DWA computes a set of trajectories and selects the one that maximizes progress toward the goal while ensuring the robot avoids collisions.

The velocities \(v\) and \(\omega\) are constrained within bounds, as shown in Equation \eqref{eq:dwa_constraints}:

\begin{equation}
\label{eq:dwa_constraints}
v_{min} \leq v \leq v_{max}, \quad \omega_{min} \leq \omega \leq \omega_{max}
\end{equation}

The objective function \(G(v, \omega)\) evaluates the alignment with the goal, distance to obstacles, and forward velocity, as described in Equation \eqref{eq:dwa_objective}:

\begin{equation}
\label{eq:dwa_objective}
G(v, \omega) = \alpha \cdot \text{heading}(v, \omega) + \beta \cdot \text{clearance}(v, \omega) + \gamma \cdot v
\end{equation}

While DWA is efficient and handles real-time obstacle avoidance well, it struggles with dynamic obstacles due to its lack of future obstacle movement prediction. The extensive velocity sampling can lead to increased computation times in complex environments.

Recent enhancements to DWA focus on improving computational efficiency and addressing the limitations in dynamic environments. A faster implementation of DWA based on non-discrete path representation \cite{lin2023faster} reduces the computational complexity by eliminating discrete path representations and employing polar coordinate transformations. Another improved version integrates reinforcement learning (RL) techniques \cite{zhou2022improved}, dynamically adjusting the sampling window size to better handle obstacles in real-time, which improves efficiency and accuracy in dynamic environments.

\subsection{Timed Elastic Band (TEB)}
TEB models the robot’s trajectory as a dynamic band that adjusts to avoid obstacles while satisfying kinodynamic constraints. The trajectory is continuously optimized using a cost function that takes into account the goal, collisions, and system dynamics.

The cost function \(J(\mathbf{x}, \mathbf{v})\) over the series of poses \(\mathbf{x}\) and velocities \(\mathbf{v}\) is defined in Equation \eqref{eq:teb_cost}:

\begin{equation}
\label{eq:teb_cost}
J(\mathbf{x}, \mathbf{v}) = \sum_{i=1}^{n-1} \left( \text{cost}_{\text{goal}}(x_i) + \text{cost}_{\text{collision}}(x_i) + \text{cost}_{\text{kinodynamics}}(v_i) \right)
\end{equation}

TEB is effective at generating smooth trajectories that adapt to obstacles and kinodynamic constraints. However, in highly dynamic environments, TEB's computational complexity can increase significantly. Additionally, its performance is sensitive to initial conditions and parameter tuning.

Recent improvements to TEB incorporate dynamic obstacle velocities using Kalman filtering to predict obstacle movement and optimize the trajectory in real time. This improved TEB method \cite{chen2021dynamic} enhances real-time performance by reducing the overall computational burden while maintaining a high success rate for dynamic obstacle avoidance.

\subsection{Model Predictive Control (MPC)}
MPC computes optimal control inputs over a prediction horizon by solving an optimization problem that accounts for both system dynamics and environmental constraints. Given the system model \(x_{k+1} = f(x_k, u_k)\), MPC minimizes the cost function defined in Equation \eqref{eq:mpc_cost}:

\begin{equation}
\label{eq:mpc_cost}
J(\mathbf{u}) = \sum_{k=0}^{N-1} \left( (x_k - x_{\text{ref},k})^\top Q (x_k - x_{\text{ref},k}) + u_k^\top R u_k \right)
\end{equation}

MPC offers smooth, optimized control over nonlinear dynamics, making it ideal for complex environments. However, it is computationally demanding, especially in real-time applications. Additionally, MPC requires highly accurate models of the robot and environment, which may not always be feasible in dynamic situations.

\subsection{Move Base Flex (MBF)}
MBF is a flexible framework in ROS that enables the integration of multiple global and local planners. It provides interfaces for different types of planners, recovery behaviors, and global path planning. The performance of MBF is dependent on the planners it integrates, and while it offers modularity, its capabilities in dynamic environments are inherited from the chosen planners (e.g., DWA, TEB).

MBF provides great flexibility but may suffer from the limitations of the specific planners it incorporates, such as limited performance in dynamic environments with fast-moving obstacles.

\subsection{Agile and Safe Pursuit (ASAP)}
ASAP uses pursuit-based control combined with safety constraints, allowing the robot to track a path while maintaining agility and avoiding obstacles. The control law minimizes the error between the robot’s current position and the pursuit point \(P(t)\) on the path, as defined in Equation \eqref{eq:asap_control}:

\begin{equation}
\label{eq:asap_control}
u(t) = \text{argmin} \| x(t) - P(t) \|
\end{equation}

With the safety constraint shown in Equation \eqref{eq:asap_safety}:

\begin{equation}
\label{eq:asap_safety}
\| P(t) - x_{\text{obs}}(t) \| \geq d_{\text{safe}}
\end{equation}

ASAP provides fast and agile movement while maintaining safety, but it struggles with complex nonlinear dynamics and requires careful tuning of the safety constraints to avoid overly conservative behavior.

\subsection{Reinforcement Learning (RL)-based Planners}
In recent years, RL-based planners have gained significant attention due to their ability to learn optimal behaviors in dynamic and complex environments. These planners do not rely on explicit models but instead learn from trial and error by interacting with the environment. RL-based planners can adapt to new environments, making them highly effective for dynamic obstacle avoidance.

However, RL-based planners face challenges in real-time applications due to the extensive training time required and the need for vast amounts of data. Additionally, their performance can be inconsistent if the training environment does not closely resemble the real-world application. Despite these challenges, RL-based planners show promise in handling complex scenarios where traditional model-based planners fall short.

\subsection{Advantages of Nonlinear Model Predictive Control (nMPC)}
nMPC addresses the shortcomings of traditional local planners by predicting future obstacle movements and directly incorporating the nonlinear dynamics of the robot. It optimizes the control inputs over a finite prediction horizon, ensuring that the robot can navigate dynamically changing environments with greater efficiency and precision.

Compared to DWA, TEB, MPC, and RL-based planners, nMPC offers improved handling of dynamic obstacles by continuously adjusting the robot's trajectory in real-time, optimizing for both safety and performance. It also handles nonlinear dynamics more effectively, making it a robust solution for highly dynamic environments.

\section{Comparison of Local Planners}

\begin{table}[h]
\centering
\caption{Evaluation of Local Planners}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Planner} & \textbf{Dynamic} & \textbf{Nonlinear} & \textbf{Real-time} \\
                 & \textbf{Obstacles} & \textbf{Dynamics}  & \textbf{Performance} \\ \hline
DWA              & Poor               & Limited            & Good                \\ \hline
TEB              & Good               & Limited            & Moderate            \\ \hline
MPC              & Good               & Good               & Poor                \\ \hline
Move Base Flex   & Inherited          & Inherited          & Modular             \\
                 & from planners      & from planners      &                     \\ \hline
ASAP             & Moderate           & Poor               & Good                \\ \hline
RL-based         & Good               & Limited            & Variable            \\ \hline
\end{tabular}
\end{table}

\bibliographystyle{IEEEtran}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Outlook}

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\columnwidth]{images/MPC_Blockdiagram_Implementation.png}
    \caption{Blockdiagram of nMPC for future Implementation }
    \label{fig:MPC_Blockdiagram_Implementation}
\end{figure}

\newblock

\begin{equation}
\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k=0}^{N-1} L(\vec{x}(k), \vec{u}(k))
\end{equation}

\begin{equation}
\label{eq:phi_definition}
\phi(\vec{x}(N)) = \frac{1}{2} \vec{x}_N^T S \vec{x}_N
\end{equation}

\begin{equation}
\label{eq:L_function}
\begin{aligned}
L(\vec{x}(k), \vec{u}(k)) = \frac{1}{2} \sum_{k}^{k+N-1} &
(\vec{x}_{R,k} - \vec{x}_{\text{ref},k})^T Q (\vec{x}_{R,k} - \vec{x}_{\text{ref},k}) \\
&+ \vec{u}_k^T R \vec{u}_k
\end{aligned}
\end{equation}

%Constraints - Control States, Collission avoidance

For safety reasons, strict limits on the control variables \(u_k\) are set in Equation \ref{eq:u_constraints} to avoid oversaturation. These limits ensure that stays within a defined range.

\begin{equation}
\label{eq:u_constraints}
\vec{u}_{\text{min}} \leq \vec{u}_k \leq \vec{u}_{\text{max}}, \quad \forall k \quad \text{…} \quad \vec{u} \in \mathbb{R}^2
\end{equation}

\begin{equation}
\label{eq:collision_condition}
-\sqrt{(x_R - x_{\text{obst}})^2 + (y_R - y_{\text{obst}})^2} + (r_R + r_{\text{obst}}) \leq 0
\end{equation}

In this equation, \( (x_{\text{obst}}, y_{\text{obst}}) \) denotes the position of an obstacle, and \( r_r + r_{\text{obst}}\) represents the sum of the radii of the robot and the obstacle, ensuring a safety margin for avoidance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Literaturverzeichnis
{\small
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,refs}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End of page 3
\clearpage

\end{document}

### 2024-09-16 src/amr_control/scripts/plot_paths.py

@@ -8,16 +8,24 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-bag_nmpc_filename = 'recorded_data_nMPC_9.bag'
-bag_dwa_filename = 'recorded_data_DWA_7.bag'
+bag_nmpc_filename = 'recorded_data_nMPC_14.bag'
+bag_dwa_filename = 'recorded_data_DWA_9.bag'
 
 # ROS topics for paths
-topic_nmpc = '/robot_path'
+topic_nmpc = '/robot_path_DWA'
 topic_dwa = '/robot_path_DWA'
 
 # Angle for cube placement along the dashed circle (in degrees)
 cube_angle_on_circle = 90  # Set the angle where you want to place the cube
 cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+
+# Drawing the environment (walls, cylinders, rectangles)
+fig, ax = plt.subplots()
+
+# Font sizes for axis labels and ticks
+axis_label_fontsize = 25
+tick_label_fontsize = 25
+
 # ---------------------------------------------------------------------------
 
 def draw_rotated_rectangle(x, y, width, height, angle, ax):
@@ -47,8 +55,6 @@ def calculate_position_on_circle(center_x, center_y, radius, angle_deg):
     y = center_y + radius * np.sin(angle_rad)
     return x, y
 
-# Drawing the environment (walls, cylinders, rectangles)
-fig, ax = plt.subplots()
 
 # Drawing walls (rectangles) as described in the SDF file
 walls = [
@@ -114,8 +120,8 @@ draw_rotated_rectangle(cube_x, cube_y, cube_size, cube_size, 0, ax)  # Cube size
 # Loading paths from ROSBAGs
 amr_control_path = roslib.packages.get_pkg_dir('amr_control')
 
-bag_nmpc_path = os.path.join(amr_control_path, f'data/{bag_nmpc_filename}')
-bag_dwa_path = os.path.join(amr_control_path, f'data/{bag_dwa_filename}')
+bag_nmpc_path = os.path.join(amr_control_path, f'data/rosbags/{bag_nmpc_filename}')
+bag_dwa_path = os.path.join(amr_control_path, f'data/rosbags/{bag_dwa_filename}')
 
 bag_nmpc = rosbag.Bag(bag_nmpc_path)
[…]

### 2024-09-16 src/amr_control/scripts/plot_paths.py
Added videos

@@ -9,14 +9,18 @@ import roslib
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
 bag_nmpc_filename = 'recorded_data_nMPC_14.bag'
-bag_dwa_filename = 'recorded_data_DWA_9.bag'
+bag_dwa_filename = 'recorded_data_DWA_8.bag'
 
 # ROS topics for paths
-topic_nmpc = '/robot_path_DWA'
+topic_nmpc = '/robot_path'
 topic_dwa = '/robot_path_DWA'
 
 # Angle for cube placement along the dashed circle (in degrees)
-cube_angle_on_circle = 90  # Set the angle where you want to place the cube
+cube_angle_on_circle_1 = 45  # Set the angle where you want to place the cube
+cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+
+# Angle for cube placement along the dashed circle (in degrees)
+cube_angle_on_circle_2 = 190  # Set the angle where you want to place the cube
 cube_size = 0.2  # Size of the cube (0.2 x 0.2)
 
 # Drawing the environment (walls, cylinders, rectangles)
@@ -114,8 +118,12 @@ dashed_circle = patches.Circle((3, 0), 0.5, linewidth=1, edgecolor='k', facecolo
 ax.add_patch(dashed_circle)
 
 # Draw a black-filled cube along the dashed circle at a specified angle
-cube_x, cube_y = calculate_position_on_circle(3, 0, 0.5, cube_angle_on_circle)  # Position along the circle
-draw_rotated_rectangle(cube_x, cube_y, cube_size, cube_size, 0, ax)  # Cube size is 0.2 x 0.2
+cube_x_1, cube_y_1 = calculate_position_on_circle(3, 0, 0.5, cube_angle_on_circle_1)  # Position along the circle
+draw_rotated_rectangle(cube_x_1, cube_y_1, cube_size, cube_size, 0, ax)  # Cube size is 0.2 x 0.2
+
+# Draw a black-filled cube along the dashed circle at a specified angle
+cube_x_2, cube_y_2 = calculate_position_on_circle(3, 0, 0.5, cube_angle_on_circle_2)  # Position along the circle
[…]

### 2024-09-19 src/amr_control/docs/paper.tex
Kein erfolg

@@
 \documentclass[conference]{IEEEtran}
+
 \IEEEoverridecommandlockouts
@@
 \usepackage[numbers,sort&compress]{natbib}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
+\cite{ASAP}
+
+\ref{fig:DWA_TEB_MPC_ASAP_path}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_path.png}
+    \caption{Blockdiagram of nMPC for future Implementation }
+    \label{fig:DWA_TEB_MPC_ASAP_path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_stats.png}
+    \caption{Blockdiagram of nMPC for future Implementation }
+    \label{fig:DWA_TEB_MPC_ASAP_stats}
+\end{figure}
+
 The Dynamic Window Approach (DWA) efficiently computes safe velocities by evaluating a limited set of possible trajectories.
@@
 % Paper contribution
+This work contributes to the state-of-the-art development, of a nonlinear Model Predictive Controller for a mobile robot with integrated dynamic obstacle avoidance.
+
+The main objective is to design a local planner that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.
+
 This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance.
@@
 
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methods}
+
+\subsection{Reference Trajectory}
 

### 2024-09-19 src/amr_control/src/amr_control/costmap_obstacle_detection.py

@@ -1,0 +1,90 @@
+#!/usr/bin/env python3
+
+import rospy
+import numpy as np
+import cv2
+from nav_msgs.msg import OccupancyGrid
+
+class ObstacleAvoidance:
+    def __init__(self):
+        rospy.init_node('costmap_obstacle_avoidance', anonymous=True)
+
+        # Subscriber für die local costmap
+        self.local_costmap_sub = rospy.Subscriber('/move_base/local_costmap/costmap', OccupancyGrid, self.costmap_callback)
+        self.latest_costmap_data = None  # Speichert die neuesten Costmap-Daten
+
+        # Skalierungsfaktor für das Bild
+        self.scale_factor = 10  # Erhöhe den Skalierungsfaktor für größere Darstellung
+
+        print("Costmap Obstacle Avoidance Node initialized.")
+
+    def costmap_callback(self, data):
+        """Callback-Funktion, die die neuesten Costmap-Daten speichert."""
+        self.latest_costmap_data = data
+
+    def process_costmap(self):
+        """Verarbeitet die Costmap-Daten, konvertiert sie in ein OpenCV-Bild und extrahiert Kreise."""
+        if self.latest_costmap_data is None:
+            return None
+
+        # Extrahiere Costmap-Daten
+        costmap_array = np.array(self.latest_costmap_data.data).reshape((self.latest_costmap_data.info.height, self.latest_costmap_data.info.width))
+
+        # Filtern wir die "blauen" Bereiche heraus. Angenommen, Blau wird durch Zellenwerte zwischen 50 und 70 dargestellt.
+        # Du kannst diesen Wertebereich anpassen, um genau das "Blau" zu repräsentieren, das du in RViz siehst.
+        blue_mask = np.logical_and(costmap_array >= 50, costmap_array <= 70)
+
+        # Konvertiere die gefilterte Costmap in ein Bild
+        costmap_image = np.zeros(costmap_array.shape, dtype=np.uint8)
+        costmap_image[blue_mask] = 255  # Die blauen Zellen werden weiß dargestellt
+
+        # Verwende findContours, um die äußersten Konturen der "blauen" Bereiche zu extrahieren
+        contours, _ = cv2.findContours(costmap_image, cv2.RETR_EXTERNAL, cv2.CHAIN_APPROX_SIMPLE)
+
+        # Erstelle ein leeres Bild zum Zeichnen der Konturen
+        contour_image = np.zeros_like(costmap_image)
+
+        # Zeichne die Konturen auf das Bild
[…]

### 2024-09-19 src/amr_control/src/amr_control/obstacle_detection.py

@@ -3,7 +3,7 @@
 import rospy
 import numpy as np
 import cv2
-from sensor_msgs.msg import LaserScan
+from nav_msgs.msg import OccupancyGrid
 from std_msgs.msg import Float32MultiArray
 from dynamic_reconfigure.server import Server
 from amr_control.cfg import ObstacleDetectionConfig  # Importiere die .cfg-Datei
@@ -17,126 +17,103 @@ class ObstacleDetection:
         self.tf_listener = tf.TransformListener()
 
         # Load parameters from YAML configuration
-        self.search_radius = rospy.get_param('trajectory_planner/prediction_distance', 2.0)  # Prediction distance
-        self.safety_corner_diam = rospy.get_param('obstacle_detection/safety_corner_diam', 0.1)  # Prediction distance
-        self.quality_level = rospy.get_param('obstacle_detection/quality_level', 0.01)  # Prediction distance
-        self.max_corners = rospy.get_param('obstacle_detection/max_corners', 20)  # Prediction distance
-        self.min_distance = rospy.get_param('obstacle_detection/min_distance', 20)  # Prediction distance
-        self.loop_rate = rospy.get_param('obstacle_detection/loop_rate', 1)  # Prediction distance
-        self.max_objects = rospy.get_param('nmpc_controller/max_obstacles', 10)  # Maximum number of obstacles
-        self.search_angle = rospy.get_param('obstacle_detection/search_angle', 90)  # Suchkegelwinkel in Grad
+        self.search_radius = rospy.get_param('trajectory_planner/prediction_distance', 2.0)
+        self.safety_corner_diam = rospy.get_param('obstacle_detection/safety_corner_diam', 0.1)
+        self.quality_level = rospy.get_param('obstacle_detection/quality_level', 0.01)
+        self.max_corners = rospy.get_param('obstacle_detection/max_corners', 20)
+        self.min_distance = rospy.get_param('obstacle_detection/min_distance', 20)
+        self.loop_rate = rospy.get_param('obstacle_detection/loop_rate', 1)
+        self.max_objects = rospy.get_param('nmpc_controller/max_obstacles', 10)
+        self.search_angle = rospy.get_param('obstacle_detection/search_angle', 90)
 
         # Initialize ROS publishers and subscribers
-        self.lidar_sub = rospy.Subscriber('/scan', LaserScan, self.lidar_callback)
[…]

### 2024-09-19 src/amr_control/src/amr_control/trajectory_planner.py

@@ -223,15 +223,16 @@ class TrajectoryPlanner:
         end_time = rospy.Time.now()  # Endzeit mit ROS-Zeitstempel
         loop_time = (end_time - start_time).to_sec()  # Taktzeit berechnen in Sekunden
 
-        if loop_time > 0.1:
-            rospy.logwarn(f"Cycle Time: {loop_time:.4f} Seconds")
-        else:
-            # Ausgabe der Taktzeit und der durchschnittlichen Taktzeit
-            rospy.loginfo(f"Cycle Time: {loop_time:.4f} SekSecondsunden")
+        # if loop_time > 0.1:
+        #     rospy.logwarn(f"Cycle Time: {loop_time:.4f} Seconds")
+        # else:
+        #     # Ausgabe der Taktzeit und der durchschnittlichen Taktzeit
+        #     rospy.loginfo(f"Cycle Time: {loop_time:.4f} SekSecondsunden")
             
     def compute_control_input(self):
         if np.linalg.norm(self.current_state - self.target_state, 2) > self.goal_tolerance:
             self.viz.create_marker_array(self.obstacles)
+            print("Obstacles: ", self.obstacles)
             self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, self.obstacles)
             
             # obs = [

### 2024-09-19 src/amr_control/src/amr_control/trajectory_interpolation_test.py
Added plot trajectory interpolation

@@ -66,19 +66,19 @@ def interpolate_trajectory(ref_traj, total_prediction_distance, N, robot_max_spe
 # Beispiel für eine Trajektorie mit Wegpunkten (x, y, yaw)
 ref_traj = np.array([
     [0, 0, 0],
-    [1, 2, 0.5],
-    [2, 3, 1.0],
-    [4, 5, 1.5],
-    [5, 6, 2.0],
-    [6, 7, 2.5],
-    [7, 7, 2.0],
-    [8, 8, 2.0],
-    [9, 9, 2.0],
+    # [1, 2, 0.5],
+    # [2, 3, 1.0],
+    # [4, 5, 1.5],
+    [5, 5, np.pi / 2],
+    # [6, 7, 2.5],
+    # [7, 7, 2.0],
+    # [8, 8, 2.0],
+    [7, 10, np.pi],
 ])
 
 # Parameter für die Interpolation
 total_prediction_distance = 15  # Gesamtdistanz für die MPC-Prediction
-N = 9  # Anzahl der Prediction-Punkte im MPC
+N = 10  # Anzahl der Prediction-Punkte im MPC
 current_speed = 0.5  # Aktuelle Geschwindigkeit des Roboters
 robot_max_speed = 1.0  # Maximale Geschwindigkeit des Roboters
 

### 2024-09-20 src/amr_control/scripts/plot_paths.py
Rosbag nMPC 15

@@ -1,3 +1,5 @@
+#!/usr/bin/env python3
+
 import matplotlib.pyplot as plt
 import matplotlib.patches as patches
 from matplotlib.transforms import Affine2D
@@ -10,38 +12,34 @@ import roslib
 # ROSBAG file paths
 bag_nmpc_filename = 'recorded_data_nMPC_14.bag'
 bag_dwa_filename = 'recorded_data_DWA_8.bag'
+# bag_teb_filename = 'recorded_data_TEB.bag'  # Add TEB file
 
-# ROS topics for paths
-topic_nmpc = '/robot_path'
-topic_dwa = '/robot_path_DWA'
+# ROS topics for cmd_vel (used by different planners)
+cmd_vel_topic = '/cmd_vel'
 
-# Angle for cube placement along the dashed circle (in degrees)
-cube_angle_on_circle_1 = 45  # Set the angle where you want to place the cube
-cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+# ------------------------- FUNCTIONS -------------------------
+def calculate_planner_frequency(bag_file_path, cmd_vel_topic):
+    """Calculate the frequency of cmd_vel messages for a planner"""
+    bag = rosbag.Bag(bag_file_path)
+    
+    # Count the number of cmd_vel messages and get the start/end times
+    cmd_vel_count = 0
+    start_time = None
+    end_time = None
 
-# Angle for cube placement along the dashed circle (in degrees)
-cube_angle_on_circle_2 = 190  # Set the angle where you want to place the cube
-cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+    for topic, msg, t in bag.read_messages(topics=[cmd_vel_topic]):
+        if start_time is None:
+            start_time = t  # Record the time of the first message
+        end_time = t  # Update the end time with each message
+        cmd_vel_count += 1
 
-# Drawing the environment (walls, cylinders, rectangles)
-fig, ax = plt.subplots()
-
-# Font sizes for axis labels and ticks
-axis_label_fontsize = 25
-tick_label_fontsize = 25
-
-# ---------------------------------------------------------------------------
-
[…]

### 2024-09-20 src/amr_control/scripts/path_recorder.py
Rosbag DWA 10

@@ -16,6 +16,7 @@ class PathRecorder:
         # Publisher für den Path
         self.path_pub_nMPC = rospy.Publisher('/robot_path_nMPC', Path, queue_size=10)
         self.path_pub_DWA = rospy.Publisher('/robot_path_DWA', Path, queue_size=10)
+        self.path_pub_TEB = rospy.Publisher('/robot_path_TEB', Path, queue_size=10)
 
         # Erstelle eine Path-Nachricht
         self.path = Path()
@@ -36,6 +37,7 @@ class PathRecorder:
         # Veröffentliche den Pfad
         self.path_pub_nMPC.publish(self.path)
         self.path_pub_DWA.publish(self.path)
+        self.path_pub_TEB.publish(self.path)
         
     def run(self):
         rospy.spin()

### 2024-09-20 src/amr_control/scripts/plot_paths.py
Rosbag TEB 2 und 3

@@ -10,9 +10,9 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-bag_nmpc_filename = 'recorded_data_nMPC_14.bag'
-bag_dwa_filename = 'recorded_data_DWA_8.bag'
-# bag_teb_filename = 'recorded_data_TEB.bag'  # Add TEB file
+bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
+bag_dwa_filename = 'recorded_data_DWA_10.bag'
+bag_teb_filename = 'recorded_data_TEB_2.bag'
 
 # ROS topics for cmd_vel (used by different planners)
 cmd_vel_topic = '/cmd_vel'
@@ -50,13 +50,6 @@ def process_path_data(path_msg):
         path_y.append(pose.pose.position.y)
     return path_x, path_y
 
-# Function to calculate the position on the circle based on the angle
-def calculate_position_on_circle(center_x, center_y, radius, angle_deg):
-    angle_rad = np.radians(angle_deg)
-    x = center_x + radius * np.cos(angle_rad)
-    y = center_y + radius * np.sin(angle_rad)
-    return x, y
-
 # Function to draw rotated rectangles (used for cubes and other shapes)
 def draw_rotated_rectangle(x, y, width, height, angle, ax):
     """Draw a rotated rectangle."""
@@ -75,20 +68,21 @@ def main():
     # Full paths to the bags
     bag_nmpc_path = os.path.join(amr_control_path, f'data/rosbags/{bag_nmpc_filename}')
     bag_dwa_path = os.path.join(amr_control_path, f'data/rosbags/{bag_dwa_filename}')
-    # bag_teb_path = os.path.join(amr_control_path, f'data/rosbags/{bag_teb_filename}')
+    bag_teb_path = os.path.join(amr_control_path, f'data/rosbags/{bag_teb_filename}')
 
     # Calculate cmd_vel frequencies for each planner
     nmpc_cmd_vel_count, nmpc_total_time, nmpc_frequency = calculate_planner_frequency(bag_nmpc_path, cmd_vel_topic)
     dwa_cmd_vel_count, dwa_total_time, dwa_frequency = calculate_planner_frequency(bag_dwa_path, cmd_vel_topic)
[…]

### 2024-09-20 src/amr_control/scripts/plot_paths.py
Rosbag TEB 5

@@ -16,6 +16,19 @@ bag_teb_filename = 'recorded_data_TEB_2.bag'
 
 # ROS topics for cmd_vel (used by different planners)
 cmd_vel_topic = '/cmd_vel'
+global_plan_topic = '/move_base/NavfnROS/plan'
+
+# Angle for cube placement along the dashed circle (in degrees)
+cube_angle_on_circle_1 = 45  # Set the angle where you want to place the cube
+cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+
+# Angle for cube placement along the dashed circle (in degrees)
+cube_angle_on_circle_2 = 190  # Set the angle where you want to place the cube
+cube_size = 0.2  # Size of the cube (0.2 x 0.2)
+
+# Font sizes for axis labels and ticks
+axis_label_fontsize = 25
+tick_label_fontsize = 25
 
 # ------------------------- FUNCTIONS -------------------------
 def calculate_planner_frequency(bag_file_path, cmd_vel_topic):
@@ -41,8 +54,8 @@ def calculate_planner_frequency(bag_file_path, cmd_vel_topic):
     else:
         return 0, 0, 0  # If no messages were found
 
-# Process path data from ROSBAG
 def process_path_data(path_msg):
+    """Process path data from a ROS message."""
     path_x = []
     path_y = []
     for pose in path_msg.poses:
@@ -50,7 +63,14 @@ def process_path_data(path_msg):
         path_y.append(pose.pose.position.y)
     return path_x, path_y
 
-# Function to draw rotated rectangles (used for cubes and other shapes)
+def calculate_cross_tracking_error(global_path, local_path):
+    """Calculate the cross-tracking error between the global path and the local path."""
+    errors = []
+    for lx, ly in zip(local_path[0], local_path[1]):
+        min_distance = min([np.sqrt((lx - gx)**2 + (ly - gy)**2) for gx, gy in zip(global_path[0], global_path[1])])
+        errors.append(min_distance)
+    return errors
+
 def draw_rotated_rectangle(x, y, width, height, angle, ax):
     """Draw a rotated rectangle."""
     theta = np.radians(angle)
@@ -59,6 +79,21 @@ def draw_rotated_rectangle(x, y, width, height, angle, ax):
     t_rot = Affine2D().rotate(theta).translate(x, y) + t
[…]

### 2024-09-20 src/amr_control/scripts/plot_paths.py
Addes new plots

@@ -10,9 +10,14 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
-bag_dwa_filename = 'recorded_data_DWA_10.bag'
-bag_teb_filename = 'recorded_data_TEB_2.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
+# bag_dwa_filename = 'recorded_data_DWA_10.bag'
+# bag_teb_filename = 'recorded_data_TEB_2.bag'
+
+bag_nmpc_filename = 'recorded_data_nMPC_17.bag'
+bag_dwa_filename = 'recorded_data_DWA_12.bag'
+bag_teb_filename = 'recorded_data_TEB_6.bag'
+
 
 # ROS topics for cmd_vel (used by different planners)
 cmd_vel_topic = '/cmd_vel'
@@ -27,8 +32,8 @@ cube_angle_on_circle_2 = 190  # Set the angle where you want to place the cube
 cube_size = 0.2  # Size of the cube (0.2 x 0.2)
 
 # Font sizes for axis labels and ticks
-axis_label_fontsize = 25
-tick_label_fontsize = 25
+axis_label_fontsize = 50
+tick_label_fontsize = 50
 
 # ------------------------- FUNCTIONS -------------------------
 def calculate_planner_frequency(bag_file_path, cmd_vel_topic):
@@ -53,6 +58,27 @@ def calculate_planner_frequency(bag_file_path, cmd_vel_topic):
         return cmd_vel_count, total_time, frequency
     else:
         return 0, 0, 0  # If no messages were found
+    
+def calculate_average_computation_time(bag_file_path, cmd_vel_topic):
+    """Calculate the average computation time between cmd_vel messages for a planner."""
+    bag = rosbag.Bag(bag_file_path)
+    
+    timestamps = []  # List to store timestamps of each cmd_vel message
+
+    # Iterate through the cmd_vel messages and record the timestamps
+    for topic, msg, t in bag.read_messages(topics=[cmd_vel_topic]):
+        timestamps.append(t.to_sec())  # Store time in seconds
+
+    bag.close()
+
+    # Calculate time differences between consecutive timestamps
+    if len(timestamps) > 1:
+        time_diffs = np.diff(timestamps)  # Differences between consecutive timestamps
[…]

### 2024-09-21 src/amr_control/scripts/plot_paths.py
New better plots

@@ -10,13 +10,13 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-# bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
-# bag_dwa_filename = 'recorded_data_DWA_10.bag'
-# bag_teb_filename = 'recorded_data_TEB_2.bag'
+bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
+bag_dwa_filename = 'recorded_data_DWA_10.bag'
+bag_teb_filename = 'recorded_data_TEB_2.bag'
 
-bag_nmpc_filename = 'recorded_data_nMPC_17.bag'
-bag_dwa_filename = 'recorded_data_DWA_12.bag'
-bag_teb_filename = 'recorded_data_TEB_6.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_16.bag'
+# bag_dwa_filename = 'recorded_data_DWA_12.bag'
+# bag_teb_filename = 'recorded_data_TEB_6.bag'
 
 
 # ROS topics for cmd_vel (used by different planners)
@@ -122,7 +122,6 @@ def calculate_position_on_circle(center_x, center_y, radius, angle_deg):
     return x, y
 
 # ------------------------- MAIN PROGRAM -------------------------
-# ------------------------- MAIN PROGRAM -------------------------
 def main():
     # Path to the ROSBAG directory
     amr_control_path = roslib.packages.get_pkg_dir('amr_control')
@@ -226,7 +225,7 @@ def main():
     bag_global.close()
 
     # Plot global plan
-    ax1.plot(global_path_x, global_path_y, label='Global Plan', color='black', linestyle=':', linewidth=2)
+    ax1.plot(global_path_x, global_path_y, label='Global Plan', color='black', linestyle=':', linewidth=4)
 
     # Extracting the paths for nMPC, DWA, and TEB
     nmpc_path_x, nmpc_path_y = [], []
@@ -251,10 +250,11 @@ def main():
         teb_path_x, teb_path_y = process_path_data(msg)
     bag_teb.close()
 
-    # Plotting the paths
-    ax1.plot(nmpc_path_x, nmpc_path_y, label='nMPC Path', color='green', linestyle='-', linewidth=2)
-    ax1.plot(dwa_path_x, dwa_path_y, label='DWA Path', color='red', linestyle='--', linewidth=2)
[…]

### 2024-09-21 src/amr_control/scripts/plot_paths.py
TEB Frequency rate is false calculated, DWA is between 10-20 Hz

@@ -12,7 +12,7 @@ import roslib
 # ROSBAG file paths
 bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
 bag_dwa_filename = 'recorded_data_DWA_10.bag'
-bag_teb_filename = 'recorded_data_TEB_2.bag'
+bag_teb_filename = 'recorded_data_TEB_7.bag'
 
 # bag_nmpc_filename = 'recorded_data_nMPC_16.bag'
 # bag_dwa_filename = 'recorded_data_DWA_12.bag'

### 2024-09-21 src/amr_control/scripts/plot_paths.py
nMPC_16_vs_DWA_12_vs_TEB_9 & nMPC_15_vs_DWA_10_vs_TEB_8

@@ -10,13 +10,13 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
-bag_dwa_filename = 'recorded_data_DWA_10.bag'
-bag_teb_filename = 'recorded_data_TEB_7.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
+# bag_dwa_filename = 'recorded_data_DWA_10.bag'
+# bag_teb_filename = 'recorded_data_TEB_8.bag'
 
-# bag_nmpc_filename = 'recorded_data_nMPC_16.bag'
-# bag_dwa_filename = 'recorded_data_DWA_12.bag'
-# bag_teb_filename = 'recorded_data_TEB_6.bag'
+bag_nmpc_filename = 'recorded_data_nMPC_16.bag'
+bag_dwa_filename = 'recorded_data_DWA_12.bag'
+bag_teb_filename = 'recorded_data_TEB_9.bag'
 
 
 # ROS topics for cmd_vel (used by different planners)

### 2024-09-21 src/amr_control/scripts/move_base_execution.py
Ablation Daten

@@ -2,6 +2,7 @@
 
 import rospy
 from geometry_msgs.msg import PoseStamped
+from tf.transformations import quaternion_from_euler
 
 def send_goal():
     # Initialisiere den Knoten
@@ -21,20 +22,26 @@ def send_goal():
     goal_msg.header.stamp = rospy.Time.now()
 
     # Setze die Position (x, y, z) und Orientierung (Quaternion) des Ziels
-    goal_msg.pose.position.x = 7.0
-    goal_msg.pose.position.y = 0.0
+    goal_msg.pose.position.x = 1.5
+    goal_msg.pose.position.y = 2.0
     goal_msg.pose.position.z = 0.0
 
-    goal_msg.pose.orientation.x = 0.0
-    goal_msg.pose.orientation.y = 0.0
-    goal_msg.pose.orientation.z = 0.0
-    goal_msg.pose.orientation.w = 1.0
+    yaw = -1-57
+    q = quaternion_from_euler(0.0, 0.0, yaw)    
+    goal_msg.pose.orientation.x = q[0]
+    goal_msg.pose.orientation.y = q[1]
+    goal_msg.pose.orientation.z = q[2]
+    goal_msg.pose.orientation.w = q[3]
 
     # Veröffentliche das Ziel
     rospy.loginfo("Sending goal to /move_base_simple/goal")
     goal_pub.publish(goal_msg)
 
     rospy.sleep(1)
+
+def yaw_to_quaternion(yaw):
+    # Placeholder function to convert yaw to quaternion
+    return 0.0, 0.0, 0.0, 1.0
 
 if __name__ == '__main__':
     try:

### 2024-09-21 src/amr_control/scripts/plot_paths.py

@@ -14,9 +14,13 @@ import roslib
 # bag_dwa_filename = 'recorded_data_DWA_10.bag'
 # bag_teb_filename = 'recorded_data_TEB_8.bag'
 
-bag_nmpc_filename = 'recorded_data_nMPC_16.bag'
-bag_dwa_filename = 'recorded_data_DWA_12.bag'
-bag_teb_filename = 'recorded_data_TEB_9.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_19.bag'
+# bag_dwa_filename = 'recorded_data_DWA_12.bag'
+# bag_teb_filename = 'recorded_data_TEB_9.bag'
+
+bag_nmpc_filename = 'recorded_data_nMPC_18.bag'
+bag_dwa_filename = 'recorded_data_DWA_15.bag'
+bag_teb_filename = 'recorded_data_TEB_10.bag'
 
 
 # ROS topics for cmd_vel (used by different planners)
@@ -181,7 +185,8 @@ def main():
         (-3.11174, -1.27262, 0.278354, 0),
         (3.55449, -1.48911, 0.278354, 0),
         (-0.526371, -1.58176, 0.278354, 0),
-        (-4.12027, 0.785226, 0.278354, 0)
+        (-4.12027, 0.785226, 0.278354, 0),
+        (1.5, -0.5, 1.5/2, 0)
     ]
 
     # Drawing black-filled circles (cylinders)

### 2024-09-21 src/amr_control/src/amr_control/trajectory_planner.py

@@ -231,16 +231,14 @@ class TrajectoryPlanner:
             
     def compute_control_input(self):
         if np.linalg.norm(self.current_state - self.target_state, 2) > self.goal_tolerance:
-            self.viz.create_marker_array(self.obstacles)
-            self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, self.obstacles)
+            # self.viz.create_marker_array(self.obstacles)
+            # self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, self.obstacles)
             
-            # obs = [
-            #     [5, -0.5, 0.4],
-            #     [5.4, -0.5, 0.4],
-            #     [5.3, 0.9, 0.8 * 2]
-            # ]
-            # self.viz.create_marker_array(obs)
-            # self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, obs)
+            obs = [
+                [1.5, -0.5, 1.5]
+            ]
+            self.viz.create_marker_array(obs)
+            self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, obs)
             self.publish_cmd_vel(self.u)
         else:
             self.u = [0, 0]

### 2024-09-22 src/amr_control/src/amr_control/trajectory_interpolation_test.py
Angst

@@ -92,6 +92,9 @@ print(new_trajectory)
 # Berechnungsende
 end_time = time.time()
 
+# Increase font sizes
+plt.rcParams.update({'font.size': 40, 'axes.titlesize': 40, 'axes.labelsize': 40, 'legend.fontsize': 14, 'xtick.labelsize': 40, 'ytick.labelsize': 40})
+
 # Berechnungsdauer in Sekunden
 calculation_time = end_time - start_time
 
@@ -111,6 +114,11 @@ for i, (x, y, yaw) in enumerate(ref_traj):
 # Plotten der Orientierungspfeile für die interpolierte Trajektorie
 for i, (x, y, yaw) in enumerate(new_trajectory):
     plt.arrow(x, y, np.cos(yaw), np.sin(yaw), head_width=0.1, color='red', zorder=11)
+
+# Anzeige der Achsenbeschriftungen und Titel
+plt.xlabel('X Position [m]', fontsize=50)
+plt.ylabel('Y Position [m]', fontsize=50)
+plt.title('Original and Interpolated Trajectories', fontsize=50)
 
 # Legende
 plt.legend()

### 2024-09-22 src/amr_control/src/amr_control/trajectory_planner.py

@@ -91,7 +91,7 @@ class TrajectoryPlanner:
         # Setze das Ziel auf den letzten Punkt in der Trajektorie
         self.target_state = self.ref_traj[-1]
         
-        self.ref_traj, self.T = self.interpolate_trajectory(self.ref_traj, self.prediction_distance, self.controller.N, self.controller.v_max, 1.1)
+        self.ref_traj, self.T = self.interpolate_trajectory(self.ref_traj, self.prediction_distance, self.controller.N, self.controller.v_max)
 
 
 
@@ -129,7 +129,7 @@ class TrajectoryPlanner:
         # Rückgabe als NumPy-Array
         return np.array(waypoints_with_yaw)
     
-    def interpolate_trajectory(self, ref_traj, total_prediction_distance, N, robot_maximum_speed, scale_factor=1.5):
+    def interpolate_trajectory(self, ref_traj, total_prediction_distance, N, robot_maximum_speed):
         """
         Interpolates or reduces the given trajectory to exactly N points, including orientation (Yaw).
         Only keeps waypoints that are within the total prediction distance.
@@ -167,9 +167,6 @@ class TrajectoryPlanner:
 
         # Gesamtdistanz der Referenz-Trajektorie
         total_ref_distance = cumulative_distances_within[-1]
-
-        # Skalierte Distanz zwischen den Punkten in der Referenztrajektorie
-        scaled_total_distance = total_ref_distance * scale_factor
 
         # Berechne die Zeit für jede Vorhersage basierend auf der maximalen Geschwindigkeit
         prediction_distance = total_prediction_distance / N
@@ -231,14 +228,16 @@ class TrajectoryPlanner:
             
     def compute_control_input(self):
         if np.linalg.norm(self.current_state - self.target_state, 2) > self.goal_tolerance:
-            # self.viz.create_marker_array(self.obstacles)
-            # self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, self.obstacles)
+            self.viz.create_marker_array(self.obstacles)
+            self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, self.obstacles)
             
-            obs = [
-                [1.5, -0.5, 1.5]
-            ]
-            self.viz.create_marker_array(obs)
-            self.u = self.controller.solve_mpc(self.current_state, self.ref_traj, self.target_state, self.T, obs)
+            # obs = [
[…]

### 2024-09-22 src/amr_control/src/amr_control/controller.py
Improved Obstacle Detection

@@ -152,10 +152,6 @@ class nMPC:
         ref_traj_array = []
         
         euklidean_distance = np.linalg.norm(current_state[:2] - target_state[:2], 2)
-        # print("Target State: ", target_state)
-        # print("Current State: ", current_state)
-        # print("Euklidean Distance: ", euklidean_distance)
-        # print("")
 
         # Verwende jeden Punkt in der Referenztrajektorie
         for k in range(self.N):

### 2024-09-22 src/amr_control/src/amr_control/obstacle_detection.py

@@ -5,34 +5,28 @@ import numpy as np
 import cv2
 from sensor_msgs.msg import LaserScan
 from std_msgs.msg import Float32MultiArray
-from dynamic_reconfigure.server import Server
-from amr_control.cfg import ObstacleDetectionConfig  # Importiere die .cfg-Datei
-from amr_control.visualizer import Visualizer
-from tf.transformations import euler_from_quaternion, quaternion_from_euler
 import tf
+from tf.transformations import euler_from_quaternion
 
 class ObstacleDetection:
     def __init__(self):
         rospy.init_node('obstacle_detection', anonymous=True)
         self.tf_listener = tf.TransformListener()
 
-        # Load parameters from YAML configuration
-        self.search_radius = rospy.get_param('trajectory_planner/prediction_distance', 2.0)  # Prediction distance
-        self.safety_corner_diam = rospy.get_param('obstacle_detection/safety_corner_diam', 0.1)  # Prediction distance
-        self.quality_level = rospy.get_param('obstacle_detection/quality_level', 0.01)  # Prediction distance
-        self.max_corners = rospy.get_param('obstacle_detection/max_corners', 20)  # Prediction distance
-        self.min_distance = rospy.get_param('obstacle_detection/min_distance', 20)  # Prediction distance
-        self.loop_rate = rospy.get_param('obstacle_detection/loop_rate', 1)  # Prediction distance
-        self.max_objects = rospy.get_param('nmpc_controller/max_obstacles', 10)  # Maximum number of obstacles
-        self.search_angle = rospy.get_param('obstacle_detection/search_angle', 90)  # Suchkegelwinkel in Grad
+        # Load parameters
+        self.search_radius = rospy.get_param('trajectory_planner/prediction_distance', 2.0)
+        self.safety_corner_diam = rospy.get_param('obstacle_detection/safety_corner_diam', 0.1)
+        self.quality_level = rospy.get_param('obstacle_detection/quality_level', 0.01)
+        self.max_corners = rospy.get_param('obstacle_detection/max_corners', 20)
+        self.min_distance = rospy.get_param('obstacle_detection/min_distance', 20)
+        self.loop_rate = rospy.get_param('obstacle_detection/loop_rate', 1)
+        self.max_objects = rospy.get_param('nmpc_controller/max_obstacles', 10)
[…]

### 2024-09-22 src/amr_control/src/amr_control/optimal_control.py

@@ -27,15 +27,6 @@ from amr_control.obstacle import Obstacle
 
 def main():
     try:
-        # obstacle = Obstacle()
-        # model = RobotModel()
-        # obstacles = [
-        #     [4, 1, 0.5],
-        #     [-2, 1, 0.5],
-        #     [4, 4, 0.7],
-        #     [-4, 4, 0.7]
-        # ]
-        # controller = nMPC(model)
         TrajectoryPlanner()
         rospy.spin()
     except rospy.ROSInterruptException:

### 2024-09-22 src/amr_control/src/amr_control/obstacle_detection.py
Diagram

@@ -86,8 +86,6 @@ class ObstacleDetection:
         """Veröffentlicht erkannte Ecken als Kreise mit Koordinaten relativ zum /map-Frame."""
         obstacles_msg = Float32MultiArray()
         max_range = int(self.search_radius * 100)
-
-        obstacles = []
         
         # Hole die Transformation vom Roboter (/base_footprint) zum globalen Frame (/map)
         try:

### 2024-09-23 src/amr_control/docs/paper.tex
Servas

@@
 
-\cite{ASAP}
-
-\ref{fig:DWA_TEB_MPC_ASAP_path}
+\cite{ASAP} conducted a comprehensive comparison of its developed local planner, ASAP, with other seminal planners, including DWA, TEB, and MPC.
+In Figure \ref{fig:DWA_TEB_MPC_ASAP_path}, the performance of these planners is compared as they guide a mobile robot to follow a global path while avoiding obstacles.
 
@@
 
+In this study, \cite{ASAP} evaluated the local planners based on metrics such as arrival time, cross track error, and computation time.
+
 \begin{figure}[!h]
@@
 
-The Dynamic Window Approach (DWA) efficiently computes safe velocities by evaluating a limited set of possible trajectories.
-However, it lacks long-term trajectory optimization and struggles with dynamic obstacles due to its short prediction horizon.
-In contrast, nMPC optimizes over a longer horizon, allowing for more accurate predictions and better handling of dynamic environments.
+The findings in Figure \ref{fig:DWA_TEB_MPC_ASAP_stats} indicate that the MPC local planner achieved the shortest arrival time, while maintaining the same cross track error as the ASAP planner.
+However, when it comes to computation time, the ASAP controller was the fastest, with a processing time of just 0.2 ms, compared to DWA's 40 ms, TEB's 5 ms, and MPC's 18 ms.
+Furthermore, \cite{ASAP} highlights that the DWA planner had the highest collision rate, which also corresponds to its longer arrival time.
 
-The Timed Elastic Band (TEB) planner adjusts global paths to account for dynamic obstacles and kinodynamic constraints but can suffer from high computational demands in dense or highly dynamic environments.
-nMPC provides a more computationally efficient solution by directly incorporating system dynamics and constraints into the optimization process, improving real-time performance in dynamic environment.
-
-Move Base Flex (MBF) offers flexibility by integrating various local planners, such as DWA and TEB, but inherits their limitations in obstacle avoidance.
-By integrating nMPC into MBF, a more robust solution can be achieved, as nMPC offers superior handling of nonlinear dynamics and dynamic obstacle avoidance.
+Similarly, \cite{MPCvsTEB} performed a comparison between MPC and TEB planners.
+The study evaluated both the TEB planner and various forms of MPC in terms of arrival time, path length, control effort, and CPU time.
+The results indicated that the TEB planner and the quadratic form of MPC had comparable arrival times, around 126.9 seconds.
+However, the time-optimal MPC, which is specifically optimized for minimizing arrival time, completed the task in just 116 seconds.
+In terms of path length and control effort, both planners showed similar performance.
+However, the computational time for MPC was found to be three times higher than that of the TEB planner, demonstrating the trade-off between efficiency and computational cost.
 
 % Problem description arising from motivation (was fehlt im aktuellen sota -> vermeidung dynamischer Objekte)
-Current local planners, such as the widely used Dynamic Window Approach (DWA) in the ROS Navigation stack, are effective for static and slow-moving obstacles but fail in dynamic environments with fast-moving obstacles.
-These planners lack the ability to predict and react effectively to rapidly changing environments, leading to suboptimal performance in real-time obstacle avoidance.
+\cite{ASAP} and \cite{MPCvsTEB} illustrate promising results for the MPC as local planner, especially due to the high adaptability forming the cost function for the required needs and the model adaptability, as for example omni-drive-directional-wheels.
+However, it is shown, that the MPC planner in combination with dynamic obstacle avoidance lack in computation time.
 
@@
 \begin{equation}
-\label{eq:mpc_cost}
-J(\mathbf{u}) = \sum_{k=0}^{N-1} \left( (x_k - x_{\text{ref},k})^\top Q (x_k - x_{\text{ref},k}) + u_k^\top R u_k \right)
+\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k=0}^{N-1} L(\vec{x}(k), \vec{u}(k))
 \end{equation}
@@
 
-\section{Comparison of Local Planners}
-
-\begin{table}[h]
-\centering
-\caption{Evaluation of Local Planners}
-\begin{tabular}{|l|c|c|c|}
-\hline
-\textbf{Planner} & \textbf{Dynamic} & \textbf{Nonlinear} & \textbf{Real-time} \\
-                 & \textbf{Obstacles} & \textbf{Dynamics}  & \textbf{Performance} \\ \hline
-DWA              & Poor               & Limited            & Good                \\ \hline
-TEB              & Good               & Limited            & Moderate            \\ \hline
-MPC              & Good               & Good               & Poor                \\ \hline
-Move Base Flex   & Inherited          & Inherited          & Modular             \\
-                 & from planners      & from planners      &                     \\ \hline
-ASAP             & Moderate           & Poor               & Good                \\ \hline
-RL-based         & Good               & Limited            & Variable            \\ \hline
-\end{tabular}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Reference Trajectory}
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_Local_Planner_Diagram_2.png}
+    \caption{ }
+    \label{fig:nMPC_Local_Planner_Diagram_2}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation Detail}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Results}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Outlook}
+\subsection{nMPC}
 
@@
 
-\newblock
+\begin{equation}\label{eq:state_vector}
+    \mathbf{x} = \begin{bmatrix} x & y & \theta \end{bmatrix}^T
+\end{equation}
+
+\begin{equation}\label{eq:control_vector}
+    u = \begin{bmatrix}
+    v & \omega
+\end{bmatrix}^T
+\end{equation}
 
 \begin{equation}
-\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k=0}^{N-1} L(\vec{x}(k), \vec{u}(k))
+\label{eq:L_function}
+\begin{aligned}
+\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k}^{k+N-1} &
+(\vec{x}_{R,k} - \vec{x}_{\text{ref},k})^T Q (\vec{x}_{R,k} - \vec{x}_{\text{ref},k}) \\
+&+ \vec{u}_k^T R \vec{u}_k
+\end{aligned}
 \end{equation}
+
+\begin{align}
+\text{subject to: } \quad \vec{x}(k+1) &= f(\vec{x}(k), \vec{u}(k)), \\
+\vec{x}(0) &= \vec{x}_0, \\
+\vec{u}(k) &\in U, \quad \forall k \in [0, N-1], \\
+\vec{x}(k) &\in X, \quad \forall k \in [0, N].
+\end{align}
 
@@
 \begin{equation}
-\label{eq:L_function}
-\begin{aligned}
-L(\vec{x}(k), \vec{u}(k)) = \frac{1}{2} \sum_{k}^{k+N-1} &
-(\vec{x}_{R,k} - \vec{x}_{\text{ref},k})^T Q (\vec{x}_{R,k} - \vec{x}_{\text{ref},k}) \\
-&+ \vec{u}_k^T R \vec{u}_k
-\end{aligned}
+\label{eq:u_constraints}
+\vec{u}_{\text{min}} \leq \vec{u}_k \leq \vec{u}_{\text{max}}, \quad \forall k \quad \text{…} \quad \vec{u} \in \mathbb{R}^2
 \end{equation}
 
-%Constraints - Control States, Collission avoidance
+\begin{equation} \label{eq:1}
+    x_{k+1} = Ax_k + Bu_k
+\end{equation}
 
-For safety reasons, strict limits on the control variables \(u_k\) are set in Equation \ref{eq:u_constraints} to avoid oversaturation. These limits ensure that stays within a defined range.
-
-\begin{equation}
-\label{eq:u_constraints}
-\vec{u}_{\text{min}} \leq \vec{u}_k \leq \vec{u}_{\text{max}}, \quad \forall k \quad \text{…} \quad \vec{u} \in \mathbb{R}^2
+\begin{equation} \label{eq:discrete_state_space_equation_DDMR}
+\begin{bmatrix}
+    x_{k+1} \\
+    y_{k+1} \\
+    \theta_{k+1}
+\end{bmatrix}
+=
+\begin{bmatrix}
+    x_k \\
+    y_k \\
+    \theta_k
+\end{bmatrix}
++ \Delta T
+\begin{bmatrix}
+    \cos(\theta) & 0 \\
+    \sin(\theta) & 0 \\
+    0 & 1
+\end{bmatrix}
+u_k
 \end{equation}
@@
 
-In this equation, \( (x_{\text{obst}}, y_{\text{obst}}) \) denotes the position of an obstacle, and \( r_r + r_{\text{obst}}\) represents the sum of the radii of the robot and the obstacle, ensuring a safety margin for avoidance.
+\subsection{Trajectory Planner}
+
+\begin{algorithm}
+\caption{Trajectory Interpolation}
+\begin{algorithmic}[1]
+\REQUIRE $P = \{(x_i, y_i, \text{yaw}_i)\}$, $d_{\text{pred}}$, $N$, $v_{\text{max}}$, $\alpha$
+\ENSURE $P_{\text{new}}$, $T$
+\STATE $D_i = \sum \sqrt{(x_{i+1} - x_i)^2 + (y_{i+1} - y_i)^2}$
+\STATE Retain points where $D_i \leq d_{\text{pred}}$
+\STATE $d_{\text{point}} = \frac{d_{\text{pred}}}{N}$
+\STATE $T = \frac{d_{\text{point}}}{v_{\text{max}}}$
+\STATE $T = T \cdot \alpha$
+\STATE Interpolate $x$, $y$, and $\text{yaw}$ to get $N$ points
+\RETURN $P_{\text{new}}$, $T$
+\end{algorithmic}
+\end{algorithm}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/Interpolated_Trajectories.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{algorithm}
+\caption{Filtered Obstacle Detection}
+\begin{algorithmic}[1]
+\STATE Filter laser scan data $(r_i, \theta_i)$ using:
+\[
+r_i < r_{\text{search}} \quad \text{and} \quad \left( -\frac{\theta_{\text{search}}}{2} \leq \theta_i \leq \frac{\theta_{\text{search}}}{2} \right)
+\]
+\STATE Convert filtered data to 2D coordinates:
+\[
+x_i = r_i \cos(\theta_i), \quad y_i = r_i \sin(\theta_i)
+\]
+\STATE Create lidar image:
+\[
+x_{\text{img}} = \left( \frac{x_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}, \quad y_{\text{img}} = \left( \frac{y_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}
+\]
+\STATE Apply Gaussian blur:
+\[
+I_{\text{blur}}(x, y) = \frac{1}{2\pi \sigma^2} \exp\left(-\frac{x^2 + y^2}{2\sigma^2}\right) \otimes I_{\text{img}}(x, y)
+\]
+\STATE Detect corners using Shi-Tomasi:
+\[
+\{(x_{\text{corner}}, y_{\text{corner}})\} = \text{Shi-Tomasi}(I_{\text{blur}})
+\]
+\STATE Sort by distance:
+\[
+d_i = \sqrt{x_{\text{corner}}^2 + y_{\text{corner}}^2}
+\]
+\STATE Transform detected corners into the robot frame:
+\[
+x_{\text{trans}} = x_{\text{robot}} + (x_{\text{corner}} \cos(\text{yaw}) - y_{\text{corner}} \sin(\text{yaw}))
+\]
+\[
+y_{\text{trans}} = y_{\text{robot}} + (x_{\text{corner}} \sin(\text{yaw}) + y_{\text{corner}} \cos(\text{yaw}))
+\]
+\STATE Select $N_{\text{max}}$ closest points
+\RETURN $(x_{\text{trans}}, y_{\text{trans}}, r_{\text{corner}})$ to nMPC
+\end{algorithmic}
+\end{algorithm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Implementation Detail}
+
+The experiments were conducted on a system equipped with an AMD Ryzen 5 7600X 6-Core Processor running at a maximum clock speed of 5.45 GHz.
+The system has 12 logical CPUs (2 threads per core) and 30 GB of RAM, with no swap space configured.
+
+The experiments ran inside a Docker container, which utilized up to 4.808 GB of RAM (approximately 15.78 \% of the available memory) and had a peak CPU usage of 855.20 \%, indicating multi-core processing.
+The container handled a maximum of 393 processes during the experiments.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion and Results}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_15_vs_DWA_10_vs_TEB_8_Path.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_15_vs_DWA_10_vs_TEB_8.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_16_vs_DWA_12_vs_TEB_9_Path.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_16_vs_DWA_12_vs_TEB_9.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_18_vs_DWA_15_vs_TEB_10_Path.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/nMPC_18_vs_DWA_15_vs_TEB_10.png}
+    \caption{ }
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Outlook}
 

### 2024-09-23 src/amr_control/src/amr_control/controller.py
Soft constraint works

@@ -16,14 +16,14 @@ import math
 from amr_control.visualizer import Visualizer
 
 class nMPC:
-    def __init__(self, model, max_obstacles, N=20, Q=np.diag([1, 1, 0.001]), R=np.diag([0.5, 0.05]), T=0.3, penalty_weight=100):
+    def __init__(self, model, max_obstacles, N=20, Q=np.diag([1, 1, 0.001]), R=np.diag([0.5, 0.05]), T=0.3, penalty_weight=0.5):
         self.model = model
         self.n_obstacles = max_obstacles
         self.N = N
         self.Q = Q
         self.R = R
         self.T = T
-        self.v_min, self.v_max = -0.0, 0.2
+        self.v_min, self.v_max = 0.0, 0.2
         self.omega_min, self.omega_max = -0.2, 0.2
         self.viz = Visualizer()
         
@@ -82,6 +82,7 @@ class nMPC:
             st_next_euler = st + T * f_value  # Verwende T aus dem Parametervektor
             g = ca.vertcat(g, st_next - st_next_euler)
                             
+        epsilon = 0.1  # Small value to prevent division by zero or singularity
         # Obstacle avoidance constraints (hard and soft)
         for k in range(N + 1):
             for i in range(self.n_obstacles):
@@ -94,8 +95,10 @@ class nMPC:
                 g = ca.vertcat(g, hard_obs_constraint)  # Ensure the robot does not collide with the obstacle
 
                 # Soft constraint: penalty for proximity to obstacles
-                rob_diam = 0.6
-                soft_obs_cost = ca.fmax(0, (rob_diam / 2 + obs_diam / 2) - ca.sqrt((X[0, k] - obs_x) ** 2 + (X[1, k] - obs_y) ** 2))
+                rob_diam = 0.3
+                distance_to_obstacle = ca.sqrt((X[0, k] - obs_x) ** 2 + (X[1, k] - obs_y) ** 2)
+                # soft_obs_cost = ca.fmax(0, (rob_diam / 2 + obs_diam / 2) - ca.sqrt((X[0, k] - obs_x) ** 2 + (X[1, k] - obs_y) ** 2))
+                soft_obs_cost = self.penalty_weight * (1 / (distance_to_obstacle + epsilon))  # Penalize proximity based on inverse distance
                 obj += self.penalty_weight * soft_obs_cost  # Penalize proximity to obstacles
 
         # Entscheidungsvariable zu einem Spaltenvektor machen

### 2024-09-23 src/amr_control/src/amr_control/trajectory_planner.py

@@ -48,8 +48,8 @@ class TrajectoryPlanner:
         self.timer = rospy.Timer(rospy.Duration(self.T), self.controller_loop)
         
         self.obstacles = [
-                [1, 0.3, 0.1],
-                [4, 0, 0.1]
+                [1, 0.3, 0.5],
+                [4, 0, 0.5]
                 # [3, 0.2, 0.3],
                 # [-4, 4, 0.7]
             ]

### 2024-09-23 src/amr_control/scripts/move_base_execution.py
Added soft constraints

@@ -22,11 +22,15 @@ def send_goal():
     goal_msg.header.stamp = rospy.Time.now()
 
     # Setze die Position (x, y, z) und Orientierung (Quaternion) des Ziels
-    goal_msg.pose.position.x = 1.5
-    goal_msg.pose.position.y = 2.0
+    # goal_msg.pose.position.x = 1.5
+    # goal_msg.pose.position.y = 2.0
+    # goal_msg.pose.position.z = 0.0
+    
+    goal_msg.pose.position.x = 7
+    goal_msg.pose.position.y = 0.0
     goal_msg.pose.position.z = 0.0
 
-    yaw = -1-57
+    yaw = 0
     q = quaternion_from_euler(0.0, 0.0, yaw)    
     goal_msg.pose.orientation.x = q[0]
     goal_msg.pose.orientation.y = q[1]
@@ -39,9 +43,6 @@ def send_goal():
 
     rospy.sleep(1)
 
-def yaw_to_quaternion(yaw):
-    # Placeholder function to convert yaw to quaternion
-    return 0.0, 0.0, 0.0, 1.0
 
 if __name__ == '__main__':
     try:

### 2024-09-23 src/amr_control/src/amr_control/controller.py

@@ -36,6 +36,9 @@ class nMPC:
         self.omega_max = rospy.get_param('nmpc_controller/omega_max', 0.5)  # Maximum angular velocity
         # Prediction distance
         self.prediction_distance = rospy.get_param('nmpc_controller/prediction_distance', 2.0)  # Prediction distance
+        self.robot_safety_diam = rospy.get_param('nmpc_controller/robot_safety_diam', 0.2)  # Robot safety diameter
+        self.penalty_weight = rospy.get_param('nmpc_controller/penalty_weight', 0.6)  # Penalty weight for obstacle avoidance
+        self.epsilon = rospy.get_param('nmpc_controller/epsilon', 0.1)  # Epsilon for obstacle avoidance
         
         self.viz = Visualizer()
 
@@ -59,7 +62,7 @@ class nMPC:
         U = ca.SX.sym('U', n_controls, N)
         P = ca.SX.sym('P', n_states + N * (n_states + n_controls) + self.n_obstacles * 3 + 1)
         X = ca.SX.sym('X', n_states, N + 1)
-        rob_diam = self.model.diam
+        rob_diam = self.robot_safety_diam
 
         # Definiere die Kostenfunktion
         obj = 0
@@ -95,14 +98,21 @@ class nMPC:
         terminal_state = X[:, N]  # Zustand am Ende des Horizonts
         obj += ca.mtimes([terminal_state.T, S, terminal_state]) / 2
 
-        # Hindernisvermeidungs-Constraints
+        # Obstacle avoidance constraints (hard and soft)
         for k in range(N + 1):
             for i in range(self.n_obstacles):
                 obs_x = P[-(3 * (i + 1) + 1)]
                 obs_y = P[-(3 * (i + 1))]
                 obs_diam = P[-(3 * (i + 1) - 1)]
-                obs_constraint = -ca.sqrt((X[0, k] - obs_x) ** 2 + (X[1, k] - obs_y) ** 2) + (rob_diam / 2 + obs_diam / 2)
-                g = ca.vertcat(g, obs_constraint)
+                
+                # Hard constraint: obstacle avoidance
+                hard_obs_constraint = -ca.sqrt((X[0, k] - obs_x) ** 2 + (X[1, k] - obs_y) ** 2) + (rob_diam / 2 + obs_diam / 2)
+                g = ca.vertcat(g, hard_obs_constraint)  # Ensure the robot does not collide with the obstacle
+
[…]

### 2024-09-23 src/amr_control/scripts/plot_paths.py
nMPC_22_vs_DWA_10_vs_TEB_8_Path & nMPC_23_vs_DWA_12_vs_TEB_9_Path

@@ -10,17 +10,17 @@ import roslib
 
 # ------------------------- CONFIGURABLE PARAMETERS -------------------------
 # ROSBAG file paths
-# bag_nmpc_filename = 'recorded_data_nMPC_15.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_22.bag'
 # bag_dwa_filename = 'recorded_data_DWA_10.bag'
 # bag_teb_filename = 'recorded_data_TEB_8.bag'
 
-# bag_nmpc_filename = 'recorded_data_nMPC_19.bag'
-# bag_dwa_filename = 'recorded_data_DWA_12.bag'
-# bag_teb_filename = 'recorded_data_TEB_9.bag'
+bag_nmpc_filename = 'recorded_data_nMPC_23.bag'
+bag_dwa_filename = 'recorded_data_DWA_12.bag'
+bag_teb_filename = 'recorded_data_TEB_9.bag'
 
-bag_nmpc_filename = 'recorded_data_nMPC_18.bag'
-bag_dwa_filename = 'recorded_data_DWA_15.bag'
-bag_teb_filename = 'recorded_data_TEB_10.bag'
+# bag_nmpc_filename = 'recorded_data_nMPC_18.bag'
+# bag_dwa_filename = 'recorded_data_DWA_15.bag'
+# bag_teb_filename = 'recorded_data_TEB_10.bag'
 
 
 # ROS topics for cmd_vel (used by different planners)

### 2024-09-23 src/amr_control/docs/paper.tex
Paper

@@
 
-\title{ EVALUATING MODEL PREDICTIVE CONTROL IN DIFFERENTIAL DRIVE ROBOTICS: \\ COMPREHENSIVE LITERATURE REVIEW }
+\title{nMPC Local Planner (ändert sich noch}
 
@@
 % Paper contribution
+The main objective is to design a controller that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.
 This work contributes to the state-of-the-art development, of a nonlinear Model Predictive Controller for a mobile robot with integrated dynamic obstacle avoidance.
+This work proposed a nMPC local Planner, in which the nMPC is integrated with a obstacle avoidance algorithm, with the aim of reducing computation time and increasing the performance, which is evaluated by reducing the arrival time and the cross tracking error.
 
-The main objective is to design a local planner that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.
+% The main objective is to design a local planner that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.
 
-This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance.
+% This work addresses these challenges by developing a nonlinear Model Predictive Controller (nMPC) for differential drive mobile robots, specifically designed for dynamic obstacle avoidance.
 The primary contribution is the integration of nMPC to improve real-time navigation performance in dynamic environments.
@@
 
-This paper contributes to the field by rigorously evaluating the nMPC against both DWA and recent advancements in local planning algorithms from the past five years.
+% This paper contributes to the field by rigorously evaluating the nMPC against both DWA and recent advancements in local planning algorithms from the past five years.
 The results demonstrate that the nMPC provides enhanced trajectory optimization and obstacle avoidance capabilities, filling a crucial gap in mobile robot control by addressing scenarios that existing methods have not sufficiently solved.
@@
 The rest of the paper is organized as follows: Section II discusses related work in local path planning and obstacle avoidance.
-Section III outlines the methodology used for our comparative evaluation.
-Section IV presents the results of simulations, and Section V concludes with a summary of findings and potential future research directions.
+Section III outlines the methodology used.
+Section IV describes how the methods were implemented and evaluated.
+In Chapter IV, the results of the experiments are presented.
+In Chapter V, the results are discussed and critically reflected upon.
+Chapter VI summarizes this work and gives an outlook on future research.
 
@@
 
-\subsection{Move Base Flex (MBF)}
-MBF is a flexible framework in ROS that enables the integration of multiple global and local planners.
-It provides interfaces for different types of planners, recovery behaviors, and global path planning.
-The performance of MBF is dependent on the planners it integrates, and while it offers modularity, its capabilities in dynamic environments are inherited from the chosen planners (e.g., DWA, TEB).
-
-MBF provides great flexibility but may suffer from the limitations of the specific planners it incorporates, such as limited performance in dynamic environments with fast-moving obstacles.
-
-\subsection{Agile and Safe Pursuit (ASAP)}
-ASAP uses pursuit-based control combined with safety constraints, allowing the robot to track a path while maintaining agility and avoiding obstacles.
-The control law minimizes the error between the robot’s current position and the pursuit point \(P(t)\) on the path, as defined in Equation \eqref{eq:asap_control}:
-
-\begin{equation}
-\label{eq:asap_control}
-u(t) = \text{argmin} \| x(t) - P(t) \|
-\end{equation}
-
-With the safety constraint shown in Equation \eqref{eq:asap_safety}:
-
-\begin{equation}
-\label{eq:asap_safety}
-\| P(t) - x_{\text{obs}}(t) \| \geq d_{\text{safe}}
-\end{equation}
-
-ASAP provides fast and agile movement while maintaining safety, but it struggles with complex nonlinear dynamics and requires careful tuning of the safety constraints to avoid overly conservative behavior.
-
-\subsection{Reinforcement Learning (RL)-based Planners}
-In recent years, RL-based planners have gained significant attention due to their ability to learn optimal behaviors in dynamic and complex environments.
-These planners do not rely on explicit models but instead learn from trial and error by interacting with the environment.
-RL-based planners can adapt to new environments, making them highly effective for dynamic obstacle avoidance.
-
-However, RL-based planners face challenges in real-time applications due to the extensive training time required and the need for vast amounts of data.
-Additionally, their performance can be inconsistent if the training environment does not closely resemble the real-world application.
-Despite these challenges, RL-based planners show promise in handling complex scenarios where traditional model-based planners fall short.
-
-\subsection{Advantages of Nonlinear Model Predictive Control (nMPC)}
-nMPC addresses the shortcomings of traditional local planners by predicting future obstacle movements and directly incorporating the nonlinear dynamics of the robot.
-It optimizes the control inputs over a finite prediction horizon, ensuring that the robot can navigate dynamically changing environments with greater efficiency and precision.
-
-Compared to DWA, TEB, MPC, and RL-based planners, nMPC offers improved handling of dynamic obstacles by continuously adjusting the robot's trajectory in real-time, optimizing for both safety and performance.
+Compared to DWA and TEB, MPC offers improved handling of dynamic obstacles by continuously adjusting the robot's trajectory in real-time, optimizing for both safety and performance.
 It also handles nonlinear dynamics more effectively, making it a robust solution for highly dynamic environments.
@@
 
+This section describes the methodology applied in this work, focusing on the integration of the trajectory planner, nMPC, and the Obstacle Detection Algorithm, culminating in the nMPC local planner.
+Figure \ref{fig:nMPC_Local_Planner_Diagram_2} illustrates the individual components of the nMPC local planner.
+The main elements are the trajectory planner, nMPC, and optionally, the obstacle detection algorithm, which will be explained in more detail later.
+
+The trajectory planner receives the global path from MoveBase.
+It processes the global plan into a local plan, taking into account the number of predictions and the prediction horizon length specified by the nMPC.
+After the nMPC receives the reference trajectory, the robot’s current pose, and the target state, the optimizer of the nMPC calculates the optimal control input and sends it back to the trajectory planner.
+Depending on whether the differential drive mobile robot (DDMR) has reached its target or not, the trajectory planner then sends the optimal control input \(\mathbf{u} = \begin{bmatrix} v & \omega \end{bmatrix}^\top\)
+
+The robot's absolute position is determined using AMCL, which helps eliminate cumulative slip and drift errors.
+However, a map must be created in advance.
+Based on the scan data from the LiDAR, the DDMR can detect obstacles.
+The Obstacle Detection Node filters the LiDAR data to define a search cone, reducing unnecessary computational load on the nMPC.
+It then sends the positions of the obstacles, along with the predefined safety radius of the obstacles, to the trajectory planner, which passes this information to the nMPC for further processing.
+
 \begin{figure}[!h]
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_Local_Planner_Diagram_2.png}
-    \caption{ }
+    \caption{nMPC-Local-Planner Block Diagram }
     \label{fig:nMPC_Local_Planner_Diagram_2}
@@
 
+The nMPC is responsible for planning a path based on the current pose, the target pose, and the reference trajectory, using an optimizer that not only satisfies the kinematics of a differential drive mobile robot (DDMR) but also avoids obstacles and respects limitations on control inputs and states.Figure \ref{fig:MPC_Blockdiagram_Implementation} illustrates the components of an MPC.
+
 \begin{figure}[!h]
@@
     \includegraphics[width=1\columnwidth]{images/MPC_Blockdiagram_Implementation.png}
-    \caption{Blockdiagram of nMPC for future Implementation }
+    \caption{Detailed Blockdiagram of nMPC \cite{Effects_of_roll_dynamics_for_car_stability_control_by_laguerre_functions}}
     \label{fig:MPC_Blockdiagram_Implementation}
 \end{figure}
+
+First, the Optimal Control Problem (OCP) must be converted into a Nonlinear Programming Problem (NLP) using the multiple shooting discretization method.
+The goal is to minimize the cost function in Equation \ref{eq:L_function}, which consists of the states and control actions for all predictions.
+
+\begin{equation}
+\label{eq:L_function}
+\begin{aligned}
+\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = J_{\text{obs}} + \phi(\vec{x}(N)) 
++ &\\ \sum_{k}^{k+N-1}
+(\vec{x}_{R,k} - \vec{x}_{\text{ref},k})^T Q (\vec{x}_{R,k} - \vec{x}_{\text{ref},k})&+ \vec{u}_k^T R \vec{u}_k
+\end{aligned}
+\end{equation}
+
+\begin{align}
+\text{subject to: } \quad \vec{x}(k+1) &= f(\vec{x}(k), \vec{u}(k)), \\
+\vec{x}(0) &= \vec{x}_0, \\
+\vec{u}(k) &\in U, \quad \forall k \in [0, N-1], \\
+\vec{x}(k) &\in X, \quad \forall k \in [0, N].
+\end{align}
+
+The state vector of the robot is described by Equation \ref{eq:state_vector} , and the control vector is described by Equation \ref{eq:control_vector}.
 
@@
 
-\begin{equation}
-\label{eq:L_function}
-\begin{aligned}
-\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k}^{k+N-1} &
-(\vec{x}_{R,k} - \vec{x}_{\text{ref},k})^T Q (\vec{x}_{R,k} - \vec{x}_{\text{ref},k}) \\
-&+ \vec{u}_k^T R \vec{u}_k
-\end{aligned}
-\end{equation}
-
-\begin{align}
-\text{subject to: } \quad \vec{x}(k+1) &= f(\vec{x}(k), \vec{u}(k)), \\
-\vec{x}(0) &= \vec{x}_0, \\
-\vec{u}(k) &\in U, \quad \forall k \in [0, N-1], \\
-\vec{x}(k) &\in X, \quad \forall k \in [0, N].
-\end{align}
+The equality constraints of the cost function ensure that the robot adheres to its dynamics.
+The inequality constraints enforce the limits on control inputs and guarantee that the robot avoids obstacles, as expressed in Equation \ref{eq:collision_condition}.
 
@@
 \phi(\vec{x}(N)) = \frac{1}{2} \vec{x}_N^T S \vec{x}_N
+\end{equation}
+
+\begin{equation}
+J_{\text{obs}} = \sum_{k=0}^{N} \sum_{i=1}^{n_{\text{obs}}} \frac{w_{\text{pen}}}{\sqrt{(x_k - x_{\text{obs},i})^2 + (y_k - y_{\text{obs},i})^2} + \epsilon}
 \end{equation}
@@
     \centering
-    \includegraphics[width=1\columnwidth]{images/nMPC_15_vs_DWA_10_vs_TEB_8_Path.png}
+    \includegraphics[width=1\columnwidth]{images/nMPC_22_vs_DWA_10_vs_TEB_8_Path.png}
     \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \label{fig:nMPC_22_vs_DWA_12_vs_TEB_6_Path}
 \end{figure}
@@
     \centering
-    \includegraphics[width=1\columnwidth]{images/nMPC_15_vs_DWA_10_vs_TEB_8.png}
+    \includegraphics[width=1\columnwidth]{images/nMPC_22_vs_DWA_10_vs_TEB_8.png}
     \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \label{fig:nMPC_22_vs_DWA_12_vs_TEB_6_Path}
 \end{figure}
@@
     \centering
-    \includegraphics[width=1\columnwidth]{images/nMPC_16_vs_DWA_12_vs_TEB_9_Path.png}
+    \includegraphics[width=1\columnwidth]{images/nMPC_23_vs_DWA_12_vs_TEB_9_Path.png}
     \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \label{fig:nMPC_23_vs_DWA_12_vs_TEB_6_Path}
 \end{figure}
@@
     \centering
-    \includegraphics[width=1\columnwidth]{images/nMPC_16_vs_DWA_12_vs_TEB_9.png}
+    \includegraphics[width=1\columnwidth]{images/nMPC_23_vs_DWA_12_vs_TEB_9.png}
     \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \label{fig:nMPC_23_vs_DWA_12_vs_TEB_6_Path}
 \end{figure}

### 2024-09-26 src/amr_control/scripts/plot_paths.py
Paper

@@ -93,13 +93,13 @@ def process_path_data(path_msg):
         path_y.append(pose.pose.position.y)
     return path_x, path_y
 
-def calculate_cross_tracking_error(global_path, local_path):
-    """Calculate the cross-tracking error between the global path and the local path."""
-    errors = []
-    for lx, ly in zip(local_path[0], local_path[1]):
-        min_distance = min([np.sqrt((lx - gx)**2 + (ly - gy)**2) for gx, gy in zip(global_path[0], global_path[1])])
-        errors.append(min_distance)
-    return errors
+# def calculate_cross_tracking_error(global_path, local_path):
+#     """Calculate the cross-tracking error between the global path and the local path."""
+#     errors = []
+#     for lx, ly in zip(local_path[0], local_path[1]):
+#         min_distance = min([np.sqrt((lx - gx)**2 + (ly - gy)**2) for gx, gy in zip(global_path[0], global_path[1])])
+#         errors.append(min_distance)
+#     return errors
 
 def draw_rotated_rectangle(x, y, width, height, angle, ax):
     """Draw a rotated rectangle."""

### 2025-04-25 src/amr_control/docs/paper.tex
Added docker compose file, modified CMakellists for amr_control package

@@
 \documentclass[conference]{IEEEtran}
-
 \IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{fancyhdr}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{subcaption}
-\usepackage{blindtext}
-\usepackage{microtype}
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage[numbers,sort&compress]{natbib}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
 
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Verwendete Packages
+\usepackage[utf8]{inputenc} % Zeichen-Enkodierung
+\usepackage[T1]{fontenc}    % Zeichen-Enkodierung
+\usepackage{blindtext}      % Platzhaltertexte
+\usepackage{amsmath}        % Mathematische Umgebungen und Symbole
+\usepackage{algorithm}      % Umgebung für Algorithmen
+\usepackage[noend]{algpseudocode} % Pseudocode innerhalb der Algorithmen
+\usepackage{graphicx}       % Einbinden von Grafiken
+\usepackage{xcolor}         % Farbnamen und Definition
+\usepackage{subcaption}     % Subcaption für Unterabbildungen
+\usepackage{array}
+\usepackage{geometry}
+\usepackage{hyperref} % For clickable URLs in bibliography
+\usepackage{url}      % For proper formatting of URLs
+\geometry{a4paper, margin=1in}
+\usepackage{listings}
+\lstset{
+  basicstyle=\ttfamily,
+  breaklines=true,     % Enables automatic line breaking
+  linewidth=\linewidth % Limits the width to the current line width
+}
+\usepackage[acronym]{glossaries}
+\makeglossaries
+% \setlength{\columnsep}{0.5in}
 
-% Create custom colour for text highlighting
+% \usepackage[numbers,sort&compress]{natbib}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Eigene Farben definieren
 \definecolor{twblue}{HTML}{1f497d}
@@
 
-\pagestyle{fancy}
-\fancyhf{}
-\rfoot{\thepage} % Seitenzahl im rechten Fuß
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
-\title{nMPC Local Planner (ändert sich noch}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Dokumentbeginn
+\begin{document}
+
+\title{Nonlinear Model Predictive Control-Based Local Planner with Integrated Dynamic Obstacle Avoidance for Mobile Robots}
 
 \author{\IEEEauthorblockN{\textbf{Student:} Eppacher Kevin, BSc. \textbf{PK:} 2310331013}
-        \IEEEauthorblockN{\textbf{Peer ReviewerIn:} Schweiger Simon, MSc.}
+        \IEEEauthorblockN{\textbf{Peer ReviewerIn:} Schwaiger Simon, MSc.}
 }
@@
 \begin{abstract}
-    Mobile robots are widely used in industries, households, and public spaces, such as Autonomous
-    Mobile Robots (AMRs) for transporting goods in intralogistics, vacuum/mower robots, and service
-    robots in restaurants. However, mobile robots face several challenges, including highly dynamic
-    environments, external disturbances such as slippage, which can complicate localization over 
-    long distances, and other environmental factors. The goal of this work is to develop a system that 
-    enables a mobile robot to navigate optimally and collision-free. Several established approaches,
-    such as the Dynamic Window Approach (DWA) and Move Base Flex, have already proven effective.
-    The Dynamic Window Approach limits the robot's velocity space to ensure collision avoidance, while
-    Move Base Flex provides a flexible interface for path planning and execution, allowing for the 
-    integration of different navigation frameworks. In this work, a control system is developed for 
-    dynamic obstacle avoidance using a nonlinear Model Predictive Controller (nMPC). The results are 
-    compared with the well-established Move Base DWA from ROS1. Both controllers are evaluated in a 
-    Gazebo simulation under three conditions: with static objects, with dynamically detected obstacles, 
-    and without obstacle avoidance (i.e., without laser scan).
 
-    (Results will follow...)
+% \title{nMPC-Local-Planner with Integrated Dynamic Obstacle Avoidance}
+
+Mobile robots play a crucial role in various domains, including logistics and service industries, where they must navigate dynamic environments filled with fast-moving obstacles.
+Traditional hierarchical navigation systems separate global path planning and local obstacle avoidance, with global planners focusing on static maps and local planners using real-time sensor data for immediate adjustments.
+However, local planners such as DWA, TEB, and MPC struggle in highly dynamic environments due to issues such as slow responsiveness, difficulty in handling sharp turns or dense obstacles, and high computational demands, which can result in suboptimal paths or failure to avoid collisions in real time.
+This paper proposes a nonlinear Model Predictive Controller (nMPC) integrated with an obstacle detection algorithm to improve dynamic obstacle avoidance performance.
+The nMPC framework selectively extracts only the most relevant obstacles for avoidance, reducing the computational load while maintaining safety and efficiency.
+This optimization minimizes computation time, reduces cross-track errors, and ensures effective navigation.
+Through comprehensive simulations, the nMPC demonstrated superior performance compared to state-of-the-art planners in dynamic obstacle avoidance tasks, achieving faster arrival times and lower tracking errors.
+Future work will extend the application of this controller to real-world systems, enhancing the nMPC’s adaptability to various robotic platforms.
+The project is made available on GitHub for public use and contributions at the following link: \url{https://github.com/KevinEppacher/walle\_ws.git}
 \end{abstract}
@@
 \section{Introduction}
-% Introduction to the paper’s main subject (subject = lokale Pfadplanung)
 
@@
 In dynamic environments, these robots are frequently confronted with fast-moving obstacles, which they must detect and avoid in real-time.
-The conventional approach to navigation involves the mobile robot first creating a map of its surroundings, typically using an occupancy grid to store information about static objects such as walls.
-Based on this map, a global path is planned using algorithms such as Rapidly Exploring Random Tree (RRT), which the robot subsequently follows \cite{thrun2005probabilistic}.
 
-However, it is important to note that while the global path provides an initial route, it is updated at a lower frequency compared to the local planner, which operates at a higher update rate.
-The local planner is responsible for adjusting the robot's trajectory in real-time to avoid newly detected obstacles, while still adhering to the waypoints of the global path \cite{siegwart2011autonomous}.
-This separation between global path planning and local obstacle avoidance is critical in ensuring that the robot can navigate effectively in both known and dynamic environments \cite{khatib1986real}.
+Navigation in mobile robotics is generally approached using a hierarchical paradigm, where a global planner generates a high-level path and a local planner refines this path based on real-time sensory data.
+The global planner operates over a static map, which is typically generated using techniques like occupancy grids, and focuses on finding an optimal or feasible path from the start to the goal location.
+This path is often generated by algorithms such as Dijkstra, A*, or more advanced techniques like Rapidly Exploring Random Trees (RRT) \cite{thrun2005probabilistic}.
+
+However, the global path alone is insufficient in dynamic environments where obstacles may move or change over time.
+To handle these situations, the local planner operates at a higher frequency, continuously refining the robot's trajectory to avoid newly detected obstacles, while ensuring the robot still follows the general direction of the global path.
+The local planner relies on real-time sensory input (e.g., LiDAR or camera data) to make instantaneous adjustments, balancing both collision avoidance and adherence to the global plan \cite{khatib1986real, siegwart2011autonomous}.
+
+This separation between global path planning, which is concerned with long-term planning over a static map, and local obstacle avoidance, which focuses on immediate reactive control, is key to ensuring that the robot can navigate effectively in both known and dynamic environments.
+By maintaining this hierarchical structure, robots are able to achieve long-distance navigation goals while remaining responsive to dynamic obstacles in real-time \cite{khatib1986real, siegwart2011autonomous}.
 
@@
 \cite{ASAP} conducted a comprehensive comparison of its developed local planner, ASAP, with other seminal planners, including DWA, TEB, and MPC.
-In Figure \ref{fig:DWA_TEB_MPC_ASAP_path}, the performance of these planners is compared as they guide a mobile robot to follow a global path while avoiding obstacles.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_path.png}
-    \caption{Blockdiagram of nMPC for future Implementation }
-    \label{fig:DWA_TEB_MPC_ASAP_path}
-\end{figure}
-
+In \cite{ASAP}, we compare the performance of these planners in guiding a mobile robot to follow a global path while avoiding densely placed obstacles.
 In this study, \cite{ASAP} evaluated the local planners based on metrics such as arrival time, cross track error, and computation time.
@@
     \includegraphics[width=1\columnwidth]{images/DWA_TEB_MPC_ASAP_stats.png}
-    \caption{Blockdiagram of nMPC for future Implementation }
+    \caption{Simulation results for arrival time, cross track error and computation time for DWA, TEB, MPC and ASAP (directly taken from \cite{ASAP})}
     \label{fig:DWA_TEB_MPC_ASAP_stats}
@@
 However, the time-optimal MPC, which is specifically optimized for minimizing arrival time, completed the task in just 116 seconds.
-In terms of path length and control effort, both planners showed similar performance.
-However, the computational time for MPC was found to be three times higher than that of the TEB planner, demonstrating the trade-off between efficiency and computational cost.
 
 % Problem description arising from motivation (was fehlt im aktuellen sota -> vermeidung dynamischer Objekte)
-\cite{ASAP} and \cite{MPCvsTEB} illustrate promising results for the MPC as local planner, especially due to the high adaptability forming the cost function for the required needs and the model adaptability, as for example omni-drive-directional-wheels.
-However, it is shown, that the MPC planner in combination with dynamic obstacle avoidance lack in computation time.
+Based on the findings in \cite{ASAP}, the weaknesses of the local planners DWA, TEB and MPC are highlighted, particularly in the context of dynamic obstacle avoidance.
+
+DWA faces significant challenges when obstacles are directly in front of the robot, especially in environments with narrow passages or sharp turns.
+This is due to the fact that DWA samples a wide range of speeds to find a feasible collision-free trajectory, but this method increases computation time and is prone to failure in tight spaces.
+In addition, in environments with dynamic obstacles, velocity sampling often cannot react quickly enough, making DWA less reliable in real-time applications \cite{ASAP}.
+
+TEB, known for generating smooth and collision-free paths, works by solving a non-convex optimisation problem.
+While TEB performs well in static or moderately dynamic environments, its performance degrades in highly dynamic environments due to the need for frequent re-optimisation.
+This can lead to suboptimal paths or deadlocks where the planner cannot find a valid solution, especially when obstacles move rapidly or unpredictably.
+In addition, TEB's computation time increases significantly in dense environments, further limiting its real-time applicability \cite{ASAP, MPCvsTEB}.
+
+MPC, on the other hand, provides near-optimal trajectories by predicting future robot states and optimising control inputs based on system dynamics and constraints.
+However, solving these constrained optimisation problems at each time step imposes a high computational burden, especially when a longer prediction horizon is required to handle complex or dynamic environments.
+The real-time performance of MPC is highly dependent on the available computational resources and the complexity of the environment.
+Furthermore, the effectiveness of MPC is highly dependent on an accurate model of the robot and the environment, which can be difficult to achieve in real-world scenarios with unpredictable obstacles \cite{ASAP, MPCvsTEB}.
 
@@
 The main objective is to design a controller that effectively addresses the challenges of dynamic obstacle avoidance, offering improved performance in real-time navigation within dynamic environments.
-This work contributes to the state-of-the-art development, of a nonlinear Model Predictive Controller for a mobile robot with integrated dynamic obstacle avoidance.
-This work proposed a nMPC local Planner, in which the nMPC is integrated with a obstacle avoidance algorithm, with the aim of reducing computation time and increasing the performance, which is evaluated by reducing the arrival time and the cross tracking error.
+This work contributes to the State-of-the-art development, of a nonlinear Model Predictive Controller for a mobile robot with integrated dynamic sparse obstacle avoidance.
+This work proposed an nMPC local planner, in which the nMPC is integrated with an obstacle avoidance algorithm, to reduce computation time and increase performance, which is evaluated by reducing the arrival time and the cross-tracking error.
 
@@
 
-In this section, we provide an overview of several state-of-the-art local planners, including the Dynamic Window Approach (DWA), Timed Elastic Band (TEB), Model Predictive Control (MPC), Move Base Flex (MBF), Agile and Safe Pursuit (ASAP), and Reinforcement Learning (RL)-based planners.
-We explain how these planners function and highlight their key limitations, especially when operating in dynamic environments.
-Additionally, we discuss how nonlinear Model Predictive Control (nMPC) addresses these limitations and provides improved performance.
+This section provides an overview of several state-of-the-art local controllers, including the Dynamic Window Approach (DWA), Timed Elastic Band (TEB) and Model Predictive Control (MPC).
+In contrast, nonlinear Model Predictive Control (nMPC) is presented to overcome these limitations and provide improved performance.
+
+\subsection{Preliminary Information on Optimization-Based Methods}
+
+Optimization-based methods like DWA, TEB, and MPC solve an Optimal Control Problem (OCP) by minimizing a cost function while respecting system constraints.
+The cost function is an objective measure that typically balances factors such as trajectory tracking, control effort, and obstacle avoidance.
+Its goal is to find control inputs that minimize deviation from the desired path while maintaining safety and efficiency.
+
+In OCPs, equality constraints ensure the system dynamics are followed, while inequality constraints handle limits such as collision avoidance and control input bounds.
+The problem is often discretized using methods like multiple shooting or single shooting, which transform the continuous problem into a finite-dimensional optimization problem.
+
+These optimization problems are solved in real-time using solvers such as Quadratic Programming (QP), Interior Point Optimizer (IPOPT), or Sequential Quadratic Programming (SQP), which can handle both the constraints and optimization efficiently over the prediction horizon.
 
 \subsection{Dynamic Window Approach (DWA)}
-DWA is a popular local planner that selects safe and feasible velocities by sampling translational \((v)\) and rotational \((\omega)\) velocities within a dynamic window.
+DWA is a popular local planner that selects safe and feasible velocities by sampling translational \((v)\) and rotational \((\omega)\) velocities within a dynamic window, reinitialising the current pose and velocities and the current obstacle position.
 These sampled velocities are evaluated through an objective function that balances forward movement and obstacle avoidance.
-DWA computes a set of trajectories and selects the one that maximizes progress toward the goal while ensuring the robot avoids collisions.
+DWA computes a set of trajectories and selects the one that maximizes progress toward the goal while ensuring the robot avoids collisions \cite{DWA, fox1997dynamic}.
 
-The velocities \(v\) and \(\omega\) are constrained within bounds, as shown in Equation \eqref{eq:dwa_constraints}:
+The velocities \(v\) and \(\omega\) are constrained within bounds (see Eq. \ref{eq:dwa_constraints}):
 
@@
 
-The objective function \(G(v, \omega)\) evaluates the alignment with the goal, distance to obstacles, and forward velocity, as described in Equation \eqref{eq:dwa_objective}:
+The objective function \(G(v, \omega)\) evaluates the alignment with the goal, distance to obstacles, and forward velocity (see Eq. \ref{eq:dwa_objective}):
 
@@
 While DWA is efficient and handles real-time obstacle avoidance well, it struggles with dynamic obstacles due to its lack of future obstacle movement prediction.
-The extensive velocity sampling can lead to increased computation times in complex environments.
+The extensive velocity sampling can lead to increased computation times in complex environments \cite{DWA}.
 
@@
 TEB models the robot’s trajectory as a dynamic band that adjusts to avoid obstacles while satisfying kinodynamic constraints.
-The trajectory is continuously optimized using a cost function that takes into account the goal, collisions, and system dynamics.
+The trajectory is continuously optimized using a cost function that takes into account the goal, collisions, and system dynamics \cite{inproceedings}.
 
@@
 \label{eq:teb_cost}
-J(\mathbf{x}, \mathbf{v}) = \sum_{i=1}^{n-1} \left( \text{cost}_{\text{goal}}(x_i) + \text{cost}_{\text{collision}}(x_i) + \text{cost}_{\text{kinodynamics}}(v_i) \right)
+\begin{aligned}
+J(\mathbf{x}, \mathbf{v}) = \sum_{i=1}^{n-1} \big( & \text{cost}_{\text{goal}}(x_i) + \text{cost}_{\text{collision}}(x_i) \\
+& + \text{cost}_{\text{kinodynamics}}(v_i) \big)
+\end{aligned}
 \end{equation}
@@
 Recent improvements to TEB incorporate dynamic obstacle velocities using Kalman filtering to predict obstacle movement and optimize the trajectory in real time.
-This improved TEB method \cite{chen2021dynamic} enhances real-time performance by reducing the overall computational burden while maintaining a high success rate for dynamic obstacle avoidance.
+This improved TEB method \cite{pr12050984} enhances real-time performance by reducing the overall computational burden while maintaining a high success rate for dynamic obstacle avoidance.
 
 \subsection{Model Predictive Control (MPC)}
-MPC computes optimal control inputs over a prediction horizon by solving an optimization problem that accounts for both system dynamics and environmental constraints.
-Given the system model \(x_{k+1} = f(x_k, u_k)\), MPC minimizes the cost function defined in Equation \eqref{eq:mpc_cost}:
+
+Model Predictive Control (MPC) computes optimal control inputs over a prediction horizon by solving an optimization problem that accounts for both system dynamics and environmental constraints.
+The fundamental principle of MPC is to generate a trajectory by forward-simulating the system’s dynamics over a prediction horizon, while adhering to constraints and minimizing a cost function.
+At each time step, the optimization problem is solved, and only the first control input is applied, making the process iterative and reactive to dynamic environments.
+
+The optimization problem involves the system model \(x_{k+1} = f(x_k, u_k)\), where \(x_k\) represents the system state and \(u_k\) represents the control input at time step \(k\).
+The MPC aims to minimize the cost function \(J(\vec{x}_k, \vec{u}_k)\), as shown in Equation \eqref{eq:mpc_cost}:
 
 \begin{equation}
+\label{eq:mpc_cost}
 \min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = \phi(\vec{x}(N)) + \sum_{k=0}^{N-1} L(\vec{x}(k), \vec{u}(k))
@@
 
-MPC offers smooth, optimized control over nonlinear dynamics, making it ideal for complex environments.
-However, it is computationally demanding, especially in real-time applications.
-Additionally, MPC requires highly accurate models of the robot and environment, which may not always be feasible in dynamic situations.
+where \( \phi(\vec{x}(N)) \) is the terminal cost, and \(L(\vec{x}(k), \vec{u}(k))\) represents the running cost over each time step \(k\).
+The term \( \phi(\vec{x}(N)) \) penalizes the deviation of the final state \(\vec{x}(N)\) from the desired target state, ensuring that the robot closely follows the planned trajectory by the end of the prediction horizon.
+The running cost \(L(\vec{x}(k), \vec{u}(k))\) is a quadratic function of both the state and the control input, where:
 
-Compared to DWA and TEB, MPC offers improved handling of dynamic obstacles by continuously adjusting the robot's trajectory in real-time, optimizing for both safety and performance.
-It also handles nonlinear dynamics more effectively, making it a robust solution for highly dynamic environments.
+- \( Q \) is the state weighting matrix, which penalizes deviations of the robot’s state from the desired reference trajectory.
+Larger values in \( Q \) correspond to higher penalties for errors in specific state variables, such as position or velocity.
+
+- \( R \) is the control input weighting matrix, which penalizes large or sudden control inputs. This encourages smoother and more efficient control actions, avoiding erratic behavior.
+
+- \( S \) is the terminal cost weighting matrix, which emphasizes the importance of reaching the target state at the end of the prediction horizon, ensuring that the final state is as close as possible to the desired state.
+The overall objective of the cost function is to balance minimizing the tracking error while ensuring efficient use of control inputs.
+
+Compared to DWA and TEB, MPC offers superior handling of dynamic obstacles by continuously adjusting the robot’s trajectory in real-time, optimizing for both safety and performance.
+Unlike DWA, which samples a range of velocities and often struggles with sharp turns or dense obstacle fields due to its reactive nature, MPC employs a predictive approach that anticipates future states, making it more adaptable to dynamic scenarios \cite{ASAP}.
+Additionally, while TEB excels at generating smooth paths, it frequently encounters computational challenges in complex environments, especially when faced with multiple moving obstacles.
+The non-convex optimization problem that TEB solves can result in suboptimal paths or deadlocks, particularly when obstacles move unpredictably \cite{ASAP, MPCvsTEB}.
+
+MPC, on the other hand, directly integrates the system’s nonlinear dynamics and constraints into its optimization process.
+By predicting future states and control inputs over a finite prediction horizon, MPC is capable of generating near-optimal paths that ensure collision-free navigation, even in highly dynamic environments.
+An additional advantage of the nMPC controller is its ability to enforce both hard and soft constraints.
+The soft constraints allow for minor violations (penalizing the cost function when predicted states approach obstacles), thereby guiding the robot towards safer paths.
+The hard constraints, on the other hand, guarantee a strictly collision-free trajectory by setting firm limits that cannot be breached.
+This dual-constraint structure provides flexibility in optimization while ensuring safety \cite{wan2024MultiUAVsNMPC}.
+
+However, one of the long-standing challenges of MPC has been its computational intensity.
+Solving a constrained optimization problem in real-time, especially with a large prediction horizon, demands significant computational resources \cite{MPC_ROS, Model_predictive_Controller_for_Mobile_Robot}.
+To overcome this challenge, a sparse obstacle representation is integrated into the proposed nMPC framework.
+By selectively focusing on the most relevant obstacles and discarding less critical data, the computational load is reduced, allowing for real-time performance while retaining the predictive capabilities of MPC.
+This integration not only lowers the computational cost but also enhances the planner’s ability to efficiently handle dynamic environments with high obstacle density \cite{Lindqvist2020MPC}.
 
@@
 
-This section describes the methodology applied in this work, focusing on the integration of the trajectory planner, nMPC, and the Obstacle Detection Algorithm, culminating in the nMPC local planner.
-Figure \ref{fig:nMPC_Local_Planner_Diagram_2} illustrates the individual components of the nMPC local planner.
-The main elements are the trajectory planner, nMPC, and optionally, the obstacle detection algorithm, which will be explained in more detail later.
+Figure \ref{fig:nMPC_Local_Planner_Diagram_2} illustrates the individual components of the nMPC local planner. The main elements are the trajectory planner, nMPC and the obstacle detection algorithm.
 
-The trajectory planner receives the global path from MoveBase.
+The trajectory planner receives the global path from a planner based on Dijkstra's search.
 It processes the global plan into a local plan, taking into account the number of predictions and the prediction horizon length specified by the nMPC.
-After the nMPC receives the reference trajectory, the robot’s current pose, and the target state, the optimizer of the nMPC calculates the optimal control input and sends it back to the trajectory planner.
-Depending on whether the differential drive mobile robot (DDMR) has reached its target or not, the trajectory planner then sends the optimal control input \(\mathbf{u} = \begin{bmatrix} v & \omega \end{bmatrix}^\top\)
+After the nMPC receives the reference trajectory, the robot’s current pose, and the target State, the optimizer of the nMPC calculates the optimal control signal \(\mathbf{u} = \begin{bmatrix} v & \omega \end{bmatrix}^\top\), until the target is reached.
 
-The robot's absolute position is determined using AMCL, which helps eliminate cumulative slip and drift errors.
-However, a map must be created in advance.
+The robot is localised in a predefined map using probabilistic localisation methods \cite{thrun2005probabilistic}.
 Based on the scan data from the LiDAR, the DDMR can detect obstacles.
@@
 It then sends the positions of the obstacles, along with the predefined safety radius of the obstacles, to the trajectory planner, which passes this information to the nMPC for further processing.
+By sending only the most relevant obstacles to the nMPC, the computational load is minimized, allowing for real-time decision-making.
 
@@
 
-\subsection{nMPC}
+\subsection{Nonlinear Model Predictive Controller}
 
-The nMPC is responsible for planning a path based on the current pose, the target pose, and the reference trajectory, using an optimizer that not only satisfies the kinematics of a differential drive mobile robot (DDMR) but also avoids obstacles and respects limitations on control inputs and states.Figure \ref{fig:MPC_Blockdiagram_Implementation} illustrates the components of an MPC.
+The nMPC is responsible for planning a path based on the current pose, the target pose, and the reference trajectory, using an optimizer that not only satisfies the kinematics of a differential drive mobile robot (DDMR) but also avoids obstacles and respects limitations on control inputs and States.
+Figure \ref{fig:nMPC_Blockdiagram_2} illustrates the components of an nMPC \cite{falcone2007predictive}.
 
@@
     \centering
-    \includegraphics[width=1\columnwidth]{images/MPC_Blockdiagram_Implementation.png}
-    \caption{Detailed Blockdiagram of nMPC \cite{Effects_of_roll_dynamics_for_car_stability_control_by_laguerre_functions}}
-    \label{fig:MPC_Blockdiagram_Implementation}
+    \includegraphics[width=1\columnwidth]{images/nMPC_Blockdiagram_2.png}
+    \caption{Detailed Blockdiagram of nMPC (modified from \cite{Effects_of_roll_dynamics_for_car_stability_control_by_laguerre_functions})}
+    \label{fig:nMPC_Blockdiagram_2}
 \end{figure}
@@
 First, the Optimal Control Problem (OCP) must be converted into a Nonlinear Programming Problem (NLP) using the multiple shooting discretization method.
-The goal is to minimize the cost function in Equation \ref{eq:L_function}, which consists of the states and control actions for all predictions.
+Unlike single shooting, where only the control vector is optimized and the entire system is forward-simulated, multiple shooting introduces both the control vector and the state vector as optimization variables.
+This means that not only are the control inputs \( \mathbf{u} \) optimized, but the system states \( \mathbf{x} \) at each prediction step are also included in the optimization \cite{BOCK19841603}.
+
+The cost function (see Eq.
+\ref{eq:L_function}) is not merely a summation over all time steps, but instead, each segment's dynamics must adhere to the system's model equations, expressed as equality constraints (see Fig.
+\ref{fig:nMPC_Blockdiagram_2}).
+This enforces that the model dynamics are satisfied over the entire prediction horizon, and discrepancies between predicted and simulated states are minimized, improving both stability and accuracy \cite{DIEHL2002577}.
+
+Moreover, this approach significantly enhances the computational time efficiency.
+By breaking the problem into smaller segments, the optimization solver can converge faster and more reliably, especially in the presence of complex nonlinear dynamics or large prediction horizons.
+The ability to treat state and control variables as separate optimization entities helps in avoiding divergence \cite{BOCK19841603}.
+
+The goal is to minimize the cost function (see Eq. \ref{eq:L_function}), which consists of the States and control actions for all predictions \cite{rawlings2009model}.
 
@@
 \begin{aligned}
-\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = J_{\text{obs}} + \phi(\vec{x}(N)) 
+\min_{\vec{u}_k} J(\vec{x}_k, \vec{u}_k) = J_{\text{obs}} + \phi(\vec{x}_N) 
 + &\\ \sum_{k}^{k+N-1}
@@
 
-\begin{align}
-\text{subject to: } \quad \vec{x}(k+1) &= f(\vec{x}(k), \vec{u}(k)), \\
-\vec{x}(0) &= \vec{x}_0, \\
-\vec{u}(k) &\in U, \quad \forall k \in [0, N-1], \\
-\vec{x}(k) &\in X, \quad \forall k \in [0, N].
-\end{align}
-
-The state vector of the robot is described by Equation \ref{eq:state_vector} , and the control vector is described by Equation \ref{eq:control_vector}.
-
-\begin{equation}\label{eq:state_vector}
-    \mathbf{x} = \begin{bmatrix} x & y & \theta \end{bmatrix}^T
-\end{equation}
-
-\begin{equation}\label{eq:control_vector}
-    u = \begin{bmatrix}
-    v & \omega
-\end{bmatrix}^T
-\end{equation}
-
-The equality constraints of the cost function ensure that the robot adheres to its dynamics.
-The inequality constraints enforce the limits on control inputs and guarantee that the robot avoids obstacles, as expressed in Equation \ref{eq:collision_condition}.
-
+The cost function \(J\) consists of three main components:
+\begin{itemize}
+    \item \(\phi(\vec{x}_N)\) represents the terminal cost, ensuring the final State \(\vec{x}_N\) is close to the target State, as defined in Equation \ref{eq:phi_definition} \cite{rawlings2009model}.
     \begin{equation}
@@
 
+    \item \(J_{\text{obs}}\) is a penalty term that increases the cost if the robot comes close to an obstacle, calculated according to Equation \ref{eq:J_obs} \cite{frasch2013parallel}.
+\end{itemize}
+
 \begin{equation}
+\label{eq:J_obs}
 J_{\text{obs}} = \sum_{k=0}^{N} \sum_{i=1}^{n_{\text{obs}}} \frac{w_{\text{pen}}}{\sqrt{(x_k - x_{\text{obs},i})^2 + (y_k - y_{\text{obs},i})^2} + \epsilon}
@@
 
-\begin{equation}
-\label{eq:u_constraints}
-\vec{u}_{\text{min}} \leq \vec{u}_k \leq \vec{u}_{\text{max}}, \quad \forall k \quad \text{…} \quad \vec{u} \in \mathbb{R}^2
+where \(x_{\text{obs},i}\) and \(y_{\text{obs},i}\) represent the coordinates of the \(i\)-th obstacle, and \(\epsilon\) is a small value to avoid singularities. 
+The State vector \(\mathbf{x}\) and control vector \(\mathbf{u}\) are defined in Equations \ref{eq:State_vector} and \ref{eq:control_vector}, respectively \cite{liniger2015nonlinear}.
+
+\begin{equation}\label{eq:State_vector}
+    \mathbf{x}_k = \begin{bmatrix} x_k & y_k & \theta_k \end{bmatrix}^T
 \end{equation}
 
-\begin{equation} \label{eq:1}
-    x_{k+1} = Ax_k + Bu_k
+\begin{equation}\label{eq:control_vector}
+    u_k = \begin{bmatrix}
+    v_k & \omega_k
+\end{bmatrix}^T
 \end{equation}
 
-\begin{equation} \label{eq:discrete_state_space_equation_DDMR}
+These vectors describe the position, orientation, and control inputs of the robot at each time step \(k\).
+The evolution of the State is constrained to follow the robot's kinematics, as enforced by Equation \ref{eq:discrete_dynamics} \cite{liniger2015nonlinear}.
+
+\begin{align}
+\vec{x}(k+1) &= f(\vec{x}(k), \vec{u}(k)) \label{eq:discrete_dynamics} \\
+\vec{x}(0) &= \vec{x}_0
+\end{align}
+
+For a differential drive mobile robot, the discrete State-space dynamics are modeled as shown in Equation \ref{eq:discrete_State_space_equation_DDMR} \cite{thrun2005probabilistic}.
+
+\begin{equation} \label{eq:discrete_State_space_equation_DDMR}
 \begin{bmatrix}
@@
 \begin{bmatrix}
-    \cos(\theta) & 0 \\
-    \sin(\theta) & 0 \\
+    \cos(\theta_k) & 0 \\
+    \sin(\theta_k) & 0 \\
     0 & 1
@@
 \end{equation}
+
+To ensure safe navigation, the control inputs are constrained between the bounds specified in Equation \ref{eq:u_constraints}.
+
+\begin{equation}
+\label{eq:u_constraints}
+\vec{u}_{\text{min}} \leq \vec{u}_k \leq \vec{u}_{\text{max}}, \quad \forall k
+\end{equation}
+
+In addition, a collision avoidance constraint, as shown in Equation \ref{eq:collision_condition}, ensures that the robot maintains a safe distance from obstacles.
 
@@
 
+This inequality guarantees that the robot's distance from any obstacle is greater than or equal to the sum of their radii, preventing collisions \cite{frasch2013parallel}.
+
+The control strategy computes the optimal sequence of control inputs \(\mathbf{u}_k\) by solving the NLP at each time step, taking into account the robot's current and predicted future States.
+The horizon \(N\) and the sampling time \(\Delta T\) influence how far ahead the controller predicts and adjusts the control actions.
+By combining trajectory planning, obstacle avoidance, and constrained optimization, nMPC provides an integrated approach for navigating in dynamic environments.
+
 \subsection{Trajectory Planner}
 
+The trajectory planner processes the global path provided by the global planner and transforms it into a local path that adheres to the predictive horizon \( N \) of the nMPC and the predicted distance \( d_{\text{pred}} \).
+By default, the global planner in ROS assigns the same orientation to all waypoints, which is suboptimal for precise trajectory tracking.
+To address this, the orientation of each waypoint based on the direction to the next point along the path has been implemented.
+This results in waypoints that are aligned with the trajectory, improving navigation accuracy.
+
+Once the waypoints are oriented correctly, they are passed to the trajectory interpolation algorithm.
+This algorithm ensures that the number of waypoints matches the number of nMPC predictions.
+Based on the robot's maximum linear velocity \( v_{\text{max}} \), the algorithm calculates the appropriate time stamps for the interpolated local path.
+This guarantees that the nMPC maintains the correct prediction length.
+Additionally, the time constant is multiplied by a scaling factor \( \alpha \) to generate a feedforward effect, ensuring that the reference waypoints are always ahead of the robot's current State, guiding the robot to follow the trajectory effectively.
+This technique also allows for subtle manipulation of speed along the trajectory.
+
+A plot illustrating this interpolation process is provided in Figure \ref{fig:nMPC_Interpolation_Plot}.
+In the example, three waypoints are given, and the algorithm linearly interpolates 10 points for 10 predictions.
+
 \begin{algorithm}
-\caption{Trajectory Interpolation}
+\caption{Trajectory Interpolation. Variables: $P = \{(x_i, y_i, \text{yaw}_i)\}$, $d_{\text{pred}}$, $N$, $v_{\text{max}}$, $\alpha$}
 \begin{algorithmic}[1]
-\REQUIRE $P = \{(x_i, y_i, \text{yaw}_i)\}$, $d_{\text{pred}}$, $N$, $v_{\text{max}}$, $\alpha$
-\ENSURE $P_{\text{new}}$, $T$
-\STATE $D_i = \sum \sqrt{(x_{i+1} - x_i)^2 + (y_{i+1} - y_i)^2}$
-\STATE Retain points where $D_i \leq d_{\text{pred}}$
-\STATE $d_{\text{point}} = \frac{d_{\text{pred}}}{N}$
-\STATE $T = \frac{d_{\text{point}}}{v_{\text{max}}}$
-\STATE $T = T \cdot \alpha$
-\STATE Interpolate $x$, $y$, and $\text{yaw}$ to get $N$ points
-\RETURN $P_{\text{new}}$, $T$
+\State Compute cumulative distance between points:
+\[
+D_i = \sum \sqrt{(x_{i+1} - x_i)^2 + (y_{i+1} - y_i)^2}
+\]
+\State Retain points where $D_i \leq d_{\text{pred}}$
+\State Compute interpolated distance per point:
+\[
+d_{\text{point}} = \frac{d_{\text{pred}}}{N}
+\]
+\State Compute time step based on maximum velocity:
+\[
+T = \frac{d_{\text{point}}}{v_{\text{max}}}
+\]
+\State Adjust time step with scaling factor:
+\[
+T = T \cdot \alpha
+\]
+\State Interpolate $x$, $y$, and $\text{yaw}$ to get $N$ prediction points
+\State \textbf{return} $P_{\text{new}}$, $T$
 \end{algorithmic}
 \end{algorithm}
+
+This interpolation algorithm takes the reference global path and generates \( N \) evenly spaced points along the trajectory.
+The associated time step \( T \) ensures smooth and continuous control of the robot’s motion, with feedforward control helping to keep the reference trajectory ahead of the robot’s actual State.
+This approach is analogous to the method used in the TEB Local Planner \cite{ROSMANN2017142}.
 
@@
     \includegraphics[width=1\columnwidth]{images/Interpolated_Trajectories.png}
-    \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \caption{Interpolation process: Given 3 initial waypoints, 10 linearly interpolated waypoints are generated for 10 nMPC predictions.}
+    \label{fig:nMPC_Interpolation_Plot}
 \end{figure}
 
+\subsection{Obstacle Detection}
+
+Unlike DWA and TEB, the obstacle detection algorithm does not subscribe to the local costmap but instead directly processes laser scan data.
+The laser scan data, once received, are initially filtered based on a search cone, defined by the search radius and search angle, as illustraded in Algorithm \ref{alg:Obstacle_Detection_Algorithm}.
+This filtering step helps to exclude obstacles that are behind the robot and no longer relevant.
+The nMPC is currently designed to operate only with positive linear velocities, meaning the robot is expected to move forward.
+If backward motion were required, the search angle would need to be adjusted by 180°.
+
+After filtering, the scan data are transformed into 2D coordinates to create a LiDAR image.
+The LiDAR image is then smoothed using Gaussian blur, which helps reduce noise and makes obstacle detection more robust.
+The smoothing process is critical for ensuring the corner detection algorithm functions effectively, as it eliminates irregularities and helps detect more consistent object edges.
+The Shi-Tomasi corner detection algorithm is applied to identify obstacles, by detecting corners \cite{GoodFeaturesToTrack}.
+Initially intended for corner detection, the algorithm can also detect walls or flat surfaces depending on the quality level, likely due to the inherent noise in the sensor data.
+By sending only the most relevant obstacles to the nMPC, the computational load is minimized, allowing for real-time decision-making.
+
+Once corners are detected, they are sorted by their distance from the robot.
+The detected positions are then transformed to the robot's coordinate frame.
+Finally, only the maximum number of obstacles that the nMPC can process are considered, with any additional obstacles being discarded, ensuring that the closest obstacles are considered by the planner.
+
 \begin{algorithm}
-\caption{Filtered Obstacle Detection}
+\caption{Shi-Thomas Obstacle Detection}
+\label{alg:Obstacle_Detection_Algorithm}
 \begin{algorithmic}[1]
-\STATE Filter laser scan data $(r_i, \theta_i)$ using:
+\State Filter laser scan data $(r_i, \theta_i)$ using:
 \[
@@
 \]
-\STATE Convert filtered data to 2D coordinates:
+\State Convert filtered data to 2D coordinates:
 \[
@@
 \]
-\STATE Create lidar image:
-\[
-x_{\text{img}} = \left( \frac{x_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}, \quad y_{\text{img}} = \left( \frac{y_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}
-\]
-\STATE Apply Gaussian blur:
+\State Create a LiDAR image for obstacle detection:
+\begin{align*}
+x_{\text{img}} &= \left( \frac{x_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}, \\
+y_{\text{img}} &= \left( \frac{y_i}{r_{\text{max}}} \times I_{\text{size}} \right) + \frac{I_{\text{size}}}{2}
+\end{align*}
+\State Apply Gaussian blur to smooth the image:
 \[
@@
 \]
-\STATE Detect corners using Shi-Tomasi:
+\State Detect corners using the Shi-Tomasi corner detection algorithm:
 \[
@@
 \]
-\STATE Sort by distance:
+\State Sort detected corners by distance from the robot:
 \[
@@
 \]
-\STATE Transform detected corners into the robot frame:
+\State Transform detected corners into the robot’s frame of reference:
 \[
@@
 \]
-\STATE Select $N_{\text{max}}$ closest points
-\RETURN $(x_{\text{trans}}, y_{\text{trans}}, r_{\text{corner}})$ to nMPC
+\State Select $N_{\text{max}}$ closest points
+\State \textbf{return} $(x_{\text{trans}}, y_{\text{trans}}, r_{\text{corner}})$ to nMPC
 \end{algorithmic}
@@
 
+A visual representation of the obstacle detection algorithm is shown in Figure \ref{fig:Obstacle_Detection}, illustrating how the laser scan data are filtered, converted, and processed to detect obstacles before passing the data to the nMPC.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=1\columnwidth]{images/obstacle_detection_2.png}
+    \caption{Obstacle Detection Algorithm in which the DDMR detects a cube with the scan measurement and representing it as two circles}
+    \label{fig:Obstacle_Detection}
+\end{figure}
+
+The integration of the obstacle detection algorithm with the trajectory interpolation ensures that the nMPC can safely navigate through the environment while considering both the robot’s kinematics and the presence of dynamic obstacles.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Implementation Detail}
+\subsection{CasADi}
+
+CasADi was chosen for this work due to its robust framework, which integrates with IPOPT to perform nonlinear optimizations.
+For the implementation of the nMPC, it was necessary to predefine the optimization problem in CasADi.
+This involved defining all the required matrices for the State vector, control vector, optimization variables, and weighting matrices \( Q \), \( R \) and \( S \), as well as the cost function.
+
+When the optimization problem is called, all necessary parameters are passed, including the current State, the reference trajectory, obstacles (represented as \( n \)-times \((x, y, \text{radius})\)), and the computed time constant \( T \).
+The parameter settings for the optimization solver were configured as follows:
+
+\begin{lstlisting}
+opts = {'ipopt.max_iter': 2000,
+        'ipopt.print_level': 0,
+        'print_time': 0,
+        'ipopt.acceptable_tol': 1e-8,
+        'ipopt.acceptable_obj_change_tol': 1e-6}
+\end{lstlisting}
+
+\subsection{Software Setup}
+
+The system was implemented in ROS1 due to its existing Navigation Stack, which includes State-of-the-art local planners such as DWA and TEB.
+ROS1 provides a simple and efficient way to integrate, test, and validate the nMPC alongside these well-established planners.
+Additionally, ROS1 offers an open-source platform, making it possible for the community to further test and develop the system.
+Additionally, this work was containerized using Docker to ensure a consistent development environment, simplifying deployment and facilitating collaboration.
+
+% \subsection{Evaluation Metrics}
+
+% The experiments were conducted using three key metrics:
+
+% \begin{itemize}
+%     \item Cross Tracking Error: The deviation of the robot's path from the first reference trajectory.
+%     \item Arrival Time: The time taken for the robot to reach its target waypoint.
+%     \item Computation Time: The average time required for the local planner to compute the control inputs.
+% \end{itemize}
+
+% \subsubsection{Experiment 1: Dynamic Obstacle Avoidance}
+
+% In the first experiment, the robot is tasked with navigating to a waypoint on the map.
+During this task, a dynamic obstacle moves in a circular pattern within the Gazebo simulation.
+The obstacle is detected only by the LiDAR sensors and the local costmap, but is not accounted for in the global plan.
+The update frequency of the system is reduced to 1 Hz, making the local planner responsible for most of the planning decisions, instead of the global planner.
+The performance of the three local planners—nMPC, DWA, and TEB—was measured based on the predefined metrics, with particular attention given to observing whether any of the planners collided with the rotating obstacle.
+
+% \subsubsection{Experiment 2: Narrow Passage with Static Obstacle}
+
+% In the second experiment, the robot must pass through a narrow corridor.
+However, the passage is partially blocked by a static obstacle, which is not present in the pre-mapped environment.
+Consequently, the global planner generates a plan that passes through the "invisible" obstacle, requiring the local planner to detect and avoid it.
+The performance of the local planners was again evaluated using the same metrics.
+
+% \subsubsection{Ablation Experiment: Disabled LiDAR Scans}
+
+% In the ablation experiment, each local planner is required to navigate to a target point.
+The direct path is obstructed by a mapped object, and the LiDAR scan data are disabled to test the robustness of the planners without the aid of real-time obstacle detection.
+This scenario was designed to assess how well the planners perform when relying solely on pre-mapped data.
+
+\subsection{Hardware}
 
@@
 \section{Discussion and Results}
+In this section, the results are presented in detail and evaluated on the basis of the previously defined metrics, such as cross-tracking error, arrival time and calculation time.
+It analyses how well the developed nMPC Local Planner performed in comparison to other methods such as DWA and TEB.
+In particular, the extent to which the soft and hard constraints used contributed to obstacle avoidance and the role that parameters such as prediction length and obstacle detection played in performance in dynamic environments are discussed.
+
+\subsection{Evaluation Metrics}
+
+The experiments were conducted using three key metrics:
+
+\begin{itemize}
+    % CTE
+    \item Cross Tracking Error: The CTE measures the accuracy of path tracking by calculating the minimum distance from the robot's path to the reference trajectory.
+This metric helps evaluate how well the robot follows the desired path \cite{gonzalez2015review}.
+
+    \begin{multline}
+    CTE = \frac{1}{N} \sum_{i=1}^{N} \min \Bigg( \sqrt{(x_{\text{robot}, i} - x_{\text{global}, j})^2} \\
+    + \sqrt{(y_{\text{robot}, i} - y_{\text{global}, j})^2} \Bigg)
+    \label{eq:CTE}
+    \end{multline}
+
+    where \( N \) is the total number of points along the path.
+\( (x_i, y_i) \) represents the coordinates of the actual position of the robot at point \(i\), and \( (x_{\text{ref},i}, y_{\text{ref},i}) \) are the coordinates of the reference path.
+The term inside the square root is the Euclidean distance between the actual position and the reference path at each point, and the minimum selects the closest point on the path.
+
+    % Arrival Time
+    \item Arrival Time: This metric measures the time taken for the robot to reach its target waypoint.
+It is crucial for evaluating the efficiency of local planners, especially in dynamic environments where timely responses are important \cite{werling2012optimal}.
+
+    % Computation Time
+    \item Computation Time: The average time required for the local planner to compute the control inputs is used to assess real-time performance (see Eq.
+\ref{eq:comp_time_correct}).
+This helps evaluate the planner's efficiency in generating control inputs quickly \cite{nielsen2020real}.
+
+    \begin{equation}
+    t_{\text{comp}} = \frac{1}{N-1} \sum_{i=1}^{N-1} (t_{i+1} - t_i)
+    \label{eq:comp_time_correct}
+    \end{equation}
+
+    where \( N \) is the total number of `cmd\_vel` messages, \( t_i \) is the timestamp of the \( i \)-th message, and \( t_{i+1} - t_i \) represents the time difference between consecutive messages.
+\end{itemize}
+
+\subsubsection{Experiment 1: Dynamic Obstacle Avoidance}
+
+In the first experiment, the robot is tasked with navigating to a waypoint on the map.
+During this task, a dynamic obstacle moves in a circular pattern within the Gazebo simulation.
+The obstacle is detected only by the LiDAR sensors and the local costmap, but is not accounted for in the global plan.
+The update frequency of the system is reduced to 1 Hz, making the local planner responsible for most of the planning decisions, instead of the global planner.
+The performance of the three local planners—nMPC, DWA, and TEB—was measured based on the predefined metrics, with particular attention given to observing whether any of the planners collided with the rotating obstacle.
+
+\subsubsection{Experiment 2: Narrow Passage with Static Obstacle}
+
+In the second experiment, the robot must pass through a narrow corridor.
+However, the passage is partially blocked by a static obstacle, which is not present in the pre-mapped environment.
+Consequently, the global planner generates a plan that passes through the "invisible" obstacle, requiring the local planner to detect and avoid it.
+The performance of the local planners was again evaluated using the same metrics.
+
+\subsubsection{Ablation Experiment: Disabled LiDAR Scans}
+
+In the ablation experiment, each local planner is required to navigate to a target point.
+The direct path is obstructed by a mapped object, and the LiDAR scan data are disabled to test the robustness of the planners without the aid of real-time obstacle detection.
+This scenario was designed to assess how well the planners perform when relying solely on pre-mapped data.
+
+Each experiment is first presented with an XY plot showing the paths generated by the three local planners (nMPC, DWA, and TEB) alongside the initial global path.
+Following this, a bar chart is provided that compares the three metrics—cross tracking error, computation time, and arrival time—across all three planners.
+This structure is consistently applied across all three experiments.
+
+\subsection{Experiment 1: Dynamic Obstacle Avoidance}
+
+In the first experiment in Figure \ref{fig:nMPC_22_vs_DWA_12_vs_TEB_6_Path}, the TEB planner encountered significant challenges with the rotating obstacle.
+The TEB planner entered a deadlock situation, where the elastic band surrounding the robot's path became entangled with the rotating obstacle.
+This prevented the planner from finding a valid path, resulting in a collision with the obstacle.
+Once the planner switched to recovery mode, causing the robot to rotate in place and clear the local costmap, it was able to find a new path and reach the target.
+However, this process led to an extended arrival time of over 90 seconds, which can be seen in Figure \ref{fig:nMPC_22_vs_DWA_12_vs_TEB_6}, and the cross tracking error with respect to the global path was also considerable due to the repeated rotations caused by the rotating obstacle.
+
+In contrast, both the nMPC and DWA planners successfully reached their targets in 40 and 39 seconds, respectively.
+The DWA planner achieved a slightly better cross tracking error than the nMPC (0.01 m difference), though the nMPC planner outperformed the DWA planner by being 2.3 times faster in computation time.
+While this difference is not captured in the plot, it was observed in the simulation that the DWA planner detected the obstacle only when it was directly in front of the robot, whereas the nMPC was able to predict and avoid the obstacle up to 2 meters in advance.
 
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_22_vs_DWA_10_vs_TEB_8_Path.png}
-    \caption{ }
+    \caption{Comparison of paths for nMPC, DWA, and TEB in Experiment 1}
     \label{fig:nMPC_22_vs_DWA_12_vs_TEB_6_Path}
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_22_vs_DWA_10_vs_TEB_8.png}
-    \caption{ }
-    \label{fig:nMPC_22_vs_DWA_12_vs_TEB_6_Path}
+    \caption{Metrics comparison (cross tracking error, computation time, arrival time) for nMPC, DWA, and TEB in Experiment 1}
+    \label{fig:nMPC_22_vs_DWA_12_vs_TEB_6}
 \end{figure}
+
+\subsection{Experiment 2: Narrow Passage with Static Obstacle}
+
+In contrast to Experiment 1, the TEB planner was the fastest to reach the target in Experiment 2, completing the task in 15 seconds, followed closely by the nMPC planner at 18 seconds, which can be seen in Figure \ref{fig:nMPC_23_vs_DWA_12_vs_TEB_6}.
+The DWA planner, however, took significantly longer, with an arrival time of approximately 35 seconds.
+The delay in the DWA planner was attributed to its failure to account for the static obstacle blocking the passage.
+The global planner generated a path through the obstacle, and the DWA local planner was unable to compute a correction in time, resulting in repeated collisions with the wall.
+
+Although the TEB planner reached the goal fastest, the nMPC planner achieved the lowest cross tracking error, demonstrating more precise path adherence.
+The TEB planner continued to show a consistent computation time of 5-10 ms as seen in Figure \ref{fig:nMPC_16_vs_DWA_12_vs_TEB_6}, \ref{fig:nMPC_22_vs_DWA_12_vs_TEB_6} and \ref{fig:nMPC_23_vs_DWA_12_vs_TEB_6}.
 
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_23_vs_DWA_12_vs_TEB_9_Path.png}
-    \caption{ }
+    \caption{Comparison of paths for nMPC, DWA, and TEB in Experiment 2}
     \label{fig:nMPC_23_vs_DWA_12_vs_TEB_6_Path}
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_23_vs_DWA_12_vs_TEB_9.png}
-    \caption{ }
-    \label{fig:nMPC_23_vs_DWA_12_vs_TEB_6_Path}
+    \caption{Metrics comparison (cross tracking error, computation time, arrival time) for nMPC, DWA, and TEB in Experiment 2}
+    \label{fig:nMPC_23_vs_DWA_12_vs_TEB_6}
 \end{figure}
+
+\subsection{Ablation Experiment: Lidar Scan Disabled}
+
+In the final experiment, the nMPC planner failed to reach its target, colliding with an object due to the absence of scan data.
+A key limitation of the current nMPC implementation is that when the final goal falls within the prediction horizon, the controller switches from reference tracking to point stabilization to optimize performance.
+This behavior needs to be addressed to ensure the nMPC follows the entire trajectory, rather than stopping prematurely at the prediction horizon.
+
+Despite reaching its goal, the TEB planner also collided with the object during this experiment.
+The DWA planner, in contrast, exhibited the best performance in terms of arrival time and cross tracking error when lidar scan data were disabled, demonstrating its robustness in situations where real-time obstacle detection is not available.
 
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_18_vs_DWA_15_vs_TEB_10_Path.png}
-    \caption{ }
+    \caption{Comparison of paths for nMPC, DWA, and TEB in Ablation Experiment}
     \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
@@
     \includegraphics[width=1\columnwidth]{images/nMPC_18_vs_DWA_15_vs_TEB_10.png}
-    \caption{ }
-    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6_Path}
+    \caption{Metrics comparison (cross tracking error, computation time, arrival time) for nMPC, DWA, and TEB in Ablation Experiment}
+    \label{fig:nMPC_16_vs_DWA_12_vs_TEB_6}
 \end{figure}
@@
 \section{Summary and Outlook}
+
+The results demonstrate that the nMPC with soft constraints for obstacle clearance penalization and hard constraints to ensure collision-free paths outperformed the TEB planner in dynamic environments, reducing arrival time by approximately 50 seconds.
+Compared to DWA, the nMPC was 18 seconds faster in narrow navigation tasks.
+Although the TEB planner was 2 seconds quicker in very tight passages, the nMPC achieved a lower cross-tracking error relative to the global path.
+The implemented nMPC offers a flexible local planner, configurable with prediction length, number of obstacles to avoid, and Shi-Tomasi quality level for corner detection.
+However, further improvements in computation time are necessary to avoid more obstacles without significantly impacting performance.
+Future work will involve testing the nMPC on real hardware and extending the model to control tracked vehicles using mathematical, data-driven, or hybrid models.
 

### 2025-04-25 src/amr_control/src/amr_control/optimal_control.py

@@ -26,6 +26,8 @@ from amr_control.trajectory_planner import TrajectoryPlanner
 from amr_control.obstacle import Obstacle
 
 def main():
+    print("Starting trajectory planner node...")
+
     try:
         TrajectoryPlanner()
         rospy.spin()

### 2025-04-28 src/amr_control/src/amr_control/controller.py
Clean up

@@ -19,26 +19,26 @@ class nMPC:
     def __init__(self, model):
         self.model = model
         # Prediction horizon
-        self.N = rospy.get_param('nmpc_controller/N', 15)  # Prediction horizon
+        self.N = rospy.get_param('nmpc_controller/N', 15)
         # Weighting matrices
-        Q_param = rospy.get_param('nmpc_controller/Q', [100, 100, 0.001])  # Diagonal values for Q
-        R_param = rospy.get_param('nmpc_controller/R', [0.05, 0.05])  # Diagonal values for R
-        S_param = rospy.get_param('nmpc_controller/S', [1, 1, 0.0])  # Diagonal values for terminal cost
-        self.S = np.diag(S_param)  # Convert list to diagonal matrix
-        self.Q = np.diag(Q_param)  # Convert list to diagonal matrix
-        self.R = np.diag(R_param)  # Convert list to diagonal matrix
+        Q_param = rospy.get_param('nmpc_controller/Q', [100, 100, 0.001])
+        R_param = rospy.get_param('nmpc_controller/R', [0.05, 0.05])
+        S_param = rospy.get_param('nmpc_controller/S', [1, 1, 0.0])
+        self.S = np.diag(S_param)
+        self.Q = np.diag(Q_param)
+        self.R = np.diag(R_param)
         # Maximum number of obstacles
-        self.n_obstacles = rospy.get_param('nmpc_controller/max_obstacles', 10)  # Maximum number of obstacles
+        self.n_obstacles = rospy.get_param('nmpc_controller/max_obstacles', 10)
         # Control bounds
-        self.v_min = rospy.get_param('nmpc_controller/v_min', 0.0)  # Minimum linear velocity
-        self.v_max = rospy.get_param('nmpc_controller/v_max', 0.2)  # Maximum linear velocity
-        self.omega_min = rospy.get_param('nmpc_controller/omega_min', -0.5)  # Minimum angular velocity
-        self.omega_max = rospy.get_param('nmpc_controller/omega_max', 0.5)  # Maximum angular velocity
+        self.v_min = rospy.get_param('nmpc_controller/v_min', 0.0)
+        self.v_max = rospy.get_param('nmpc_controller/v_max', 0.2)
+        self.omega_min = rospy.get_param('nmpc_controller/omega_min', -0.5)
+        self.omega_max = rospy.get_param('nmpc_controller/omega_max', 0.5)
         # Prediction distance
[…]

### 2025-04-28 src/amr_control/src/amr_control/obstacle_detection.py

@@ -37,7 +37,7 @@ class ObstacleDetection:
         lidar_ranges = np.array(data.ranges)
         lidar_angles = np.linspace(data.angle_min, data.angle_max, len(lidar_ranges))
 
-        # Berechne den Suchwinkel: +/- der Hälfte des angegebenen Suchwinkels
+        # Calculate the search angle: +/- half of the specified search angle
         search_angle_half = np.radians(self.search_angle / 2)
 
         # Filter out obstacles within the search radius and within the desired angle ranges
@@ -87,7 +87,7 @@ class ObstacleDetection:
         obstacles_msg = Float32MultiArray()
         max_range = int(self.search_radius * 100)
         
-        # Hole die Transformation vom Roboter (/base_footprint) zum globalen Frame (/map)
+        # Retrieve the transformation from the robot (/base_footprint) to the global frame (/map)
         try:
             (trans, rot) = self.tf_listener.lookupTransform('/map', '/base_footprint', rospy.Time(0))
             robot_x, robot_y = trans[0], trans[1]
@@ -96,7 +96,7 @@ class ObstacleDetection:
             rospy.logwarn("Unable to get robot pose from TF")
             return
 
-        # Berechne die Entfernung und den Winkel relativ zur Bewegungsrichtung für jede Ecke
+        # Calculate the distance and angle relative to the direction of motion for each corner
         distances = []
         for corner in corners:
             x, y = corner.ravel()

### 2025-04-28 src/amr_control/src/amr_control/trajectory_interpolation_test.py

@@ -16,117 +16,111 @@ def interpolate_trajectory(ref_traj, total_prediction_distance, N, robot_max_spe
     :return: Interpolated or reduced reference trajectory as a list of waypoints with orientation
     """
 
-    # Berechne die Distanzen zwischen den Punkten der aktuellen Referenz-Trajektorie
-    ref_points = np.array(ref_traj)[:, :2]  # Nur x, y für Distanzen berechnen
-    yaw_angles = np.array(ref_traj)[:, 2]  # Yaw-Winkel (Orientierung) separat speichern
+    # Calculate the distances between points in the current reference trajectory
+    ref_points = np.array(ref_traj)[:, :2]
+    yaw_angles = np.array(ref_traj)[:, 2]
     distances = np.sqrt(np.sum(np.diff(ref_points, axis=0) ** 2, axis=1))
     cumulative_distances = np.insert(np.cumsum(distances), 0, 0)
 
-    # Nur die Waypoints behalten, die innerhalb der totalen Prediction-Distanz liegen
+    # Keep only the waypoints within the total prediction distance
     within_distance_mask = cumulative_distances <= total_prediction_distance
     ref_points_within_distance = ref_points[within_distance_mask]
     yaw_within_distance = yaw_angles[within_distance_mask]
     cumulative_distances_within = cumulative_distances[within_distance_mask]
 
-    # Falls die Anzahl der Punkte nicht ausreicht, füge den letzten Punkt hinzu
+    # If the number of points is insufficient, add the last point
     if len(ref_points_within_distance) < 2:
         ref_points_within_distance = np.vstack([ref_points_within_distance, ref_points[-1]])
         yaw_within_distance = np.append(yaw_within_distance, yaw_angles[-1])
         cumulative_distances_within = np.append(cumulative_distances_within, total_prediction_distance)
 
-    # Gesamtdistanz der Referenz-Trajektorie
+    # Total distance of the reference trajectory
     total_ref_distance = cumulative_distances_within[-1]
 
-    # Skalierte Distanz zwischen den Punkten in der Referenztrajektorie
+    # Scaled distance between points
     scaled_total_distance = total_ref_distance * scale_factor
 
-    # Berechne die Zeit für jede Vorhersage basierend auf der maximalen Geschwindigkeit
[…]

### 2025-04-28 src/amr_control/src/amr_control/trajectory_planner.py

@@ -45,7 +45,7 @@ class TrajectoryPlanner:
         self.obstacle_sub = rospy.Subscriber('/detected_obstacles', Float32MultiArray, self.obstacle_callback)
         self.ref_traj = []
 
-        # Zusätzliche Variablen für die Zeitmessung
+        # Additional variables for time measurement
         self.total_time = 0.0
         self.loop_count = 0.0
                 
@@ -67,133 +67,116 @@ class TrajectoryPlanner:
             return None
         
     def obstacle_callback(self, msg):
-        # Extrahiere die Hindernisse aus der empfangenen Nachricht (msg.data ist eine flache Liste)
-        obstacles = np.array(msg.data).reshape(-1, 3)  # Formatiere die Daten in eine Liste von Dreiergruppen (x, y, diameter)
+        # Extract obstacles from the received message (msg.data is a flat list)
+        obstacles = np.array(msg.data).reshape(-1, 3)
         
-        # Konvertiere die NumPy-Array in eine reguläre Liste
+        # Convert the numpy array into a regular list
         self.obstacles = obstacles.tolist()
     
-    
     def global_plan_callback(self, msg):
-        # Prüfe, ob es Wegpunkte im globalen Plan gibt
+        # Check if there are waypoints in the global plan
         if len(msg.poses) == 0:
             rospy.logwarn("Received empty global plan. Skipping.")
             return
 
-        # Extrahiere (x, y, yaw) für jede Pose in der globalen Plan-Nachricht
+        # Extract (x, y, yaw) for each pose in the global plan message
         self.ref_traj = self.adjust_waypoint_orientations(msg.poses)
 
-        # Überprüfe, ob die resultierende ref_traj nach der Anpassung nicht leer ist
+        # Check if the resulting ref_traj is empty after adjustment
         if len(self.ref_traj) == 0:
             rospy.logwarn("Adjusted reference trajectory is empty. Skipping.")
             return
 
-        # Setze das Ziel auf den letzten Punkt in der Trajektorie
+        # Set the target to the last point in the trajectory
         self.target_state = self.ref_traj[-1]
         
         self.ref_traj, self.T = self.interpolate_trajectory(self.ref_traj, self.prediction_distance, self.controller.N, self.controller.v_max)
 
-
-
     def adjust_waypoint_orientations(self, poses):
         """
-        Berechnet die Orientierung (Yaw) für jede Pose basierend auf der Richtung zum nächsten Punkt.
[…]
